\begin{section_header}[orange]
	\textbf{\section{Equipment}}
\end{section_header}

\subsection{Fake SINs}\label{fake_SINs}

Fake SINs are the lifeline of any SINless runner. They allow you to shop at Stuffer Shack, walk around in public (At least in nice places), rent a house, buy gear legally, assuage the cops, get into places, and so on. Without a SIN, you are persona non grata, meaning that - while it might be considered unethical to most - you have little to no rights and can be fucked by any corpo with a chip on his shoulder.

\begin{wraptable}[25]{r}{9cm}
	\begin{center} 
		\begin{adjustwidth}{-0mm}{}
			\scalebox{1.0}{
				\begin{tabular}{|c|c|c|c|c|}
					\hline
					SIN Rating & Skill & Interval & Cost & LC \\
					\hline
					\hline
					Rating 0, Burner & 1 & Weekly & 1,800¥ & 2 \\
					Rating 1, Burner & 4 & Weekly & 2,160¥ & 2 \\
					Rating 2, Burner & 7 & Weekly & 2,520¥ & 2 \\
					Rating 3, Burner & 10 & Weekly & 3,240¥ & 1 \\
					Rating 4, Burner & 13 & Weekly & 4,680¥ & 1 \\
					Rating 5, Burner & 16 & Weekly & 7,560¥ & 1 \\
					Rating 6, Burner & 19 & Weekly & 9,000¥ & 1 \\
					\hline
					Rating 0, Default & 1 & Monthly & 5,400¥ & 1 \\
					Rating 1, Default & 4 & Monthly & 6,480¥ & 1 \\
					Rating 2, Default & 7 & Monthly & 7,560¥ & 1 \\
					Rating 3, Default & 10 & Monthly & 9,720¥ & 1 \\
					Rating 4, Default & 13 & Monthly & 14,040¥ & 1 \\
					Rating 5, Default & 16 & Monthly & 22.680¥ & 0 \\
					Rating 6, Default & 19 & Monthly & 27,000¥ & 0 \\
					\hline
					Rating 0, Lifestyle & 1 & Yearly & 9,000¥ & 1 \\
					Rating 1, Lifestyle & 4 & Yearly & 10,800¥ & 1 \\
					Rating 2, Lifestyle & 7 & Yearly & 12,600¥ & 0 \\
					Rating 3, Lifestyle & 10 & Yearly & 16,20¥ & 0 \\
					Rating 4, Lifestyle & 13 & Yearly & 23,400¥ & 0 \\
					Rating 5, Lifestyle & 16 & Yearly & 37,800¥ & 0 \\
					Rating 6, Lifestyle & 19 & Yearly & 45,000¥ & 0 \\
					\hline
				\end{tabular}
			}
		\end{adjustwidth}
	\end{center}
\end{wraptable}

Whenever it becomes important to determine whether a SIN holds up or not, the player must roll against the SIN's skill. Success means that the SIN holds, revealing no discrepancies. Critical Success means something positive happens; the GM is heavily suggested to tailor this to the situation, but a default result could be that the recent scan lends credibility to it, raising its rating by one level for its next check. 

A failure can result in the SIN being burned, with a failure by 1 or 2 usually eliciting confusion and/or further investigation by the scanner - which may serve as an opportunity to rectify the situation, or might serve as cause for increased suspicion!. Meanwhile, failure by more usually results in the SIN being automatically denied and flagged for deletion, which can have wide ranging consequences depending on the reason for the scan, but non-law enforcement individuals may be unlikely to recognize the reason behind the denial (Professional (Law Enforcement) +5, Law (Criminal) +3, or any other suitable skill at a bonus). A critical failure is extra bad; the SIN is automatically burned, and something other terrible thing happens, often being that the SIN registry alerts the authorities.

The level of scrutiny is also important when scanning a SIN. As an example, a normal tarry stop will usually provide no penalty or bonus, but distracted, quick, or non-critical scans may provide a +3 bonus, while something as uninvolved as name checks at the door or drone bulk scanning provides a +6 bonus. This is the only way for Rating 0 SINs to succeed, and skills above 16 should be considered to automatically succeed. 

On the other hand, involved scans can lower the odds, with a detention or arrest providing a -3 penalty, and something as extreme as a corporation buying data from other jurisdictions or collating long time periods can provide a -6 penalty. This is the only way for a Rating 6 SIN to fail, and skills below 4 should automatically fail.

Additionally, the SIN registries of nations constantly check for anomalies, dead individuals, and so on. While this process is one of the reasons it's possible to obtain fake SINs in the first place, it also will weed out fake identities over time. Each SIN has an Interval associated with it, representing how substantial, complex, confusing, or just difficult it is to audit the identity. After each interval of time passes, the player must roll vs the SIN's skill, with the results being the same as a normal scan.

Fake SINs come in three categories, Burner, Default, and Lifestyle. Burner SINs are ones that do not last. They are meant to serve as a short term solution rather than a permanent identity. Often times, these types of SINs are provided by Johnsons for specific runs. Default SINs are the most common kind, with a lifespan measured in months, not weeks. These can survive long enough to be lived on, while not being expensive or risky enough to prevent use when committing crimes. Lastly, lifestyle SINs are meant to serve as full identities. If you're considering these, you should also consider the Alternative Identity advantage. Regardless, these are measured in years and are likely to last the whole game as long as they aren't put under serious scrutiny.

If you want to design a fake SIN for a specific circumstance, check out the \hyperref[bts_fake_SIN]{Behind the Screen section on Fake SINs,} which provides a number of possibilities for more finely tuned IDs.

\subsubsection{Alternative Rules}

Don't forget to check out the \hyperref[setting_equipment]{Equipment section of Setting} for a number of rulings from Pyramid articles that are used in this section!

\subsection{Armor and Clothing}

A runner's armor is his best defense against bullets, but it's also just as important to wear armor that won't get you shot at in the first place! The Sixth World is one where armored clothing is relatively common (for those who can afford it), but that doesn't mean that preparing to get shot isn't noteworthy to those in the know!

\subsubsection{Reflex Armor and Clothing}

Reflex armor makes use of STF (Sheer-Thickening Fluid) to reinforce normal improved kevlar. The fluid is made up of ceramic nanoparticles suspended in non-newtonian liquids designed to stiffen on impact, carefully built into the items so as to not limit their use as normal armor and clothing, while providing advanced protection. After treatment it allows for the kevlar to stiffen up when hit, greatly improving resistance while still maintaining flexibility and maneuverability.

However, those looking for alternative solutions may take to the Magnetic Liquid design. This design uses ferrous metallic particles suspended in a carrier fluid to stiffen into metallic plates when impacts are detected by sensors. It can protect the user against a wider variety of threats, but comes at the expense of both being more expensive alongside detectable by magnetic anomaly scanners (Or any sensor that can detect ferrous metals). Flexible suits built out of this material increase their cost by 33\%, but increase their secondary DR from 1/3 to 1/2 (e.g. 12/4* increases to 12/6*).

Optionally as well, users may buy older versions of armor, made out of Improved Kevlar - which really amount to nothing more than stylized kevlar vests and suits! This can be done in one of two ways; generally, due to the bulk of such low-tech materials, armor made with Improved Kevlar would be limited to torso, elbow pads, and other locations that did not need to flex very much. In order to maintain the same amount of flexibility, such suits must \textit{halve their DR}, which also increases weight by 25\% and reduces costs to 1/3\footnote{Note that this is a generalism, for the most accurate results see Pyramid \#3-85 or: reduce DR to 44\%, increase weight by 11\%, and reduce cost to 29.7\%}. Alternatively, for bulkier suits that maintain their durability, increase weight by +150\%, reduce cost to 2/3, and worsen the level of concealability by one (e.g. Light Clothing to Normal Clothing), although DRs above 20 cannot use this method.

All armor has a modifier to its concealment equal to its DR/3+4 (HT66), which is further discussed in \hyperref[holdout]{the Holdout skill section.} As well, some armor pieces can apply bonuses to Holdout (B200), such as the Lined Coat, but these are usually assessed by the GM or noted in the description.

\begin{center} 
	\begin{adjustwidth}{-0mm}{}
		\scalebox{1.0}{
			\begin{tabular}{|c|c|c|c|c|c|c|}
				\hline
				Armor & Location & DR & Weight & Cost & LC & Notes \\
				\hline
				Actioneer Business Clothes & Torso, Groin, Legs, Arms & 12/4* & 6.4 & 1,750¥ & 3 & [1,2,3] \\ 
				Armor Clothing & Torso, Arms & 6/1* & 1.6 & 470¥ & 4 & [1,4] \\
				Armor Jacket & Torso, Arms, Skull & 15/5* & 4.4 & 1,330¥ & 3 & [1,3,5] \\
				Armor Vest & Torso & 18/6* & 3.1 & 920¥ & 3 & [1,3]\\
				Chameleon Suit & All & 4/1* & 6.19 & 4,655¥ & 3 & [1,4,6] \\
				Full Body Armor & Torso, Groin, Arms, Legs, Neck & 18/6* & 8.2 & 2,500¥ & 3 & [1,3]\\ 
				Full Helmet & Skull & 18 & 3.02 & 756¥ & 3 & \\
				\textit{+Visor} & Eyes, Face & 15 & 1.05 & 420¥ & 3 & \\
				Lined Coat & Torso, Arms & 15/5* & 3.9 & 1,170¥ & 3 & [1,3,7]\\
				Urban Explorer Jumpsuit & Torso, Groin, Arms, Legs & 9/3* & 4.1 & 1,250¥ & 3 & [1,4,9] \\
				STF Gloves & Hands & 6/2* & 0.11 & 32¥ & 3 & [1,8]\\
				\hline
			\end{tabular}
		}
	\end{adjustwidth}
\end{center}

[1] - The full DR only applies against piercing and cutting damage. Use the second DR for all other damage types.

[2] - Incorporates an Undercover Holster (HT154).

[3] - Concealable under clothing or \textit{as} normal clothing.

[4] - Concealable as light clothing or can be very easily hidden under clothes.

[5] - DR to skull only applies to Rear, when hood is up.

[6] - Incorporates Thermo-Optic Chameleon Surface (UT98).

[7] - Provides a +4 bonus to Holdout for items hidden underneath.

[8] - Extremely concealable as any very light clothing or under anything.

[9] - Includes a built in music player and Biomonitor Bracelet (UT197)

\subsubsection{Trauma Plates}

Trauma plates are small Ceramic Nanocomposite plates that are meant to cover the upper torso from threats ranging from pistol rounds to heavy rifles. They can be carried in any plate carrier, load bearing gear, or certain armors by default as indicated (Full Body Armor, etc). Most plates are designed to only cover the chest hit location (PY:85 p18; Treated as torso and covers vitals, but can be avoided through targeting Abdomen at -1. Hits to chest also have a 1/6 chance of becoming vitals hits if possible.), however there are also smaller vests that only cover vital locations, while the quite uncommon larger plates - largely only used by military or corporate soldiers - can cover the entire torso (In essence a full breastplate).

Trauma plates can also be made out of Titanium Nanocomposites, which prevent them from degrading quickly under fire at the expense of higher weight. Any plate can be made out of Titanium Nanocomposites which increases weight by 20\% and removes the semi-ablative trait.

\begin{center} 
	\begin{adjustwidth}{-0mm}{}
		\scalebox{1.0}{
			\begin{tabular}{|c|c|c|c|c|c|c|}
				\hline
				Armor & Location & DR & Weight & Cost & LC & Notes \\
				\hline
				Trauma Plate, Level I & Chest & 6F & 1.5 & 450¥ & 3 & [1] \\
				Trauma Plate, Level II & Chest & 12F & 3.1 & 950¥ & 3 & [1] \\
				Trauma Plate, Level III & Chest & 30F & 7.9 & 2,350¥ & 3 & [1] \\
				\hline
				Small Trauma Plate, Level I & Vitals & 6F & 0.3 & 90¥ & 3 & [1] \\
				Small Trauma Plate, Level II & Vitals & 12F & 0.6 & 180¥ & 3 & [1] \\
				Small Trauma Plate, Level III & Vitals & 34F & 1.7 & 510¥ & 3 & [1] \\
				\hline
				Large Trauma Plate, Level I & Torso & 6F & 2.1 & 630¥ & 3 & [1] \\
				Large Trauma Plate, Level II & Torso & 12F & 4.2 & 1,260¥ & 3 & [1] \\
				Large Trauma Plate, Level III & Torso & 30F & 10.5 & 3,150¥ & 3 & [1] \\
				\hline
			\end{tabular}
		}
	\end{adjustwidth}
\end{center}

[1] - The DR is semi-ablative.

\subsection{Weapons}

Where not noted, all firearms follow TL 9 Ultratech conventions (Such as being Malf. 17, etc.). Some noteworthy things to remember are that all firearm weights are \textit{loaded weights}, and cost also include one \textit{loaded magazine} - or full reload if the firearm lacks a magazine.

\subsubsection{Assault Cannons}

Assault Cannons are a curious development of the Sixth World, born out of the increased physical capabilities available through goblinization, cyberware, and awakenings all pushing the limits of what would traditionally be considered a small-arm. The Assault Cannons themselves are cannons (both smoothbore and rifled) designed for the form factor of a metahuman footsoldier's squad level armament while remaining loaded with large rounds traditionally used for autocannons, light-anti-tank weapons, or even light tank weaponry on the very high end. Additionally, most of them have reduced capabilities to their mounted autocannon cousins, most commonly the heavily lower capacities and the loss of fully automatic firing in favor of semi-automatic or single-shot.

Their main purpose is to utilitize the greater strength available to some Sixth World individuals in ways that allow them to either punch up against a wide range of armored and non-armored vehicles or - as is often the case with Shadowrunners - overmatch what would usually be well made defenses for small arms such as Full Body Armor or Mil-Spec Battlesuits. While they still do not excel at their anti-armour role as much as missile launchers, they bring flexibility in ways that more than make up for it.

Do note, that unlike Shadowrun Assault Cannons are entirely capable of taking normal Ammunition and Warheads, which can be found in Ultratech and High Tech - which restrictions on Gauss weaponry noted in Ultratech as well.

\textbf{GUNNER(Cannon)(DX-4, or other Gunner at -4)}
\begin{center} 
	\begin{adjustwidth}{-9.5mm}{}
		\scalebox{0.84}{
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				Weapon & Damage & Acc & Range & Weight & RoF & Shots & ST & Bulk & Rcl & Cost & LC & Notes \\
				\hline
				Ares Thunderstruck Gauss Rifle, 20mmG & 6dx3(3) pi+ & 6 & 2,200/13,000 & 40/5 & 3 & 10+1(3) & 16† & -7 & 2 & 28,000¥/100¥ & 1 & [1] \\
				Krime Cannon, 20mmCL & 7dx3 pi++ & 5 & 1,250/5,300 & 122/2 & 2 & 6(3) & 19† & -8 & 4 & 20,100¥/100¥ & 1 & [2] \\ 
				Panther XXL, 50mmCL & 4dx10 pi++ & 6 &  2,200/18,000 & 180/17 & 2 & 15+1(3) & 21† & -11 & 5 & 40,400¥/260¥ & 1 &  \\
				\hline
			\end{tabular}
		}
	\end{adjustwidth}
\end{center}

[1] - Magazine includes 6 C Cells, which have enough energy for 10 at normal power, or ~7 for a full magazine at high power (UT 141).

[2] - Built for SM+1 individuals by default, can be built for SM+2 at with only half the increased cost as normal oversizing.

\par\rule{\textwidth}{0.5pt} 

\begin{multicols}{2}
\begin{breakbox}
\textbf{Ares Thunderstruck Gauss Rifle}
	
Ares' massively successful breach into the field of practical electromagnetic rifles, the Thunderstruck has been extraordinarily asset for many combat roles and missions, seeing use from Ares Firewatch to Shadowrunners. While it doesn't pack nearly as much punch as most Cannons do for its size, it is made up for by its enhanced penetration, lighter recoil load, and quicker cycle time.

One of the standing problems with electromagnetic weaponry has been the massive amount of energy required, although it would seem that Ares has successfully managed to fix this problem. The magazines for the Thunderstruck have 5 integral C Cells, which provide enough juice for 10 shots at normal power, or 6.67 when boosted (UT 141). 

While a boosted Thunderstruck can be extremely competitive with most standard issue, it is unable to take many of the ammunition and warheads that allow Assault Cannons to exceed in specialty roles (e.g. High Explosive for anti-infantry, APFSDS for coring lightly armored targets, and so on). Often, this is not necessary, but it is a core weakness to this format.

When attached to vehicles or defense emplacements, it is often connected to external power - there is even a backpack version of the batteries. In such cases, the Thunderstruck can have its Cells removed from the magazines, reducing their weight to 2.5 lb each.

Ares has gone all in on this firearm, providing a wide selection of upgrades and attachments on order - and due to their clientele they often take the most extreme and effective suites possible.

\textbf{Krime Cannon}

One of the cheapest and harder hitting Assault Cannons on the market. Krime markets themselves towards the larger metatypes with an emphasis on attitude and firepower, however this weapon has become popular to see use outside their intended audiences. Krime will size this to any SM +1 to +2 character as part of their purchase. SM +0 can still be bought at a 70\% upcharge (See \hyperref[metatype_sizing]{the section of Unusually Sized Metatypes for reference}).

\textbf{Panther XXL}

Practically the poster child for Assault Cannons, the Panther XXL has reigned supreme for many years and still holds strong in the face of new innovation such as the Ares Thunderstruck. Being such a high caliber it's perhaps more accurate to call this a light tank cannon with a grip and stock.

It comes stock with modern Smartgun electronics, allowing it to be wielded by any professional fighting force - or deniable asset, right out of the box.
\end{breakbox}
\end{multicols}


\subsubsection{Light Machine Guns}

Light Machine Guns are rifled automatic firearms that are intended to provide a small group of individuals the rate of fire to support a variety of tactics while also denying the enemy similar ones. Often this is achieved through the use of Oportunity Fire (B390), Suppression Fire (B409), or sometimes Spraying Fire (B409), although these can - and often do - serve as high capacity replacements for normal automatic rifles.

Their weight and strength can sometimes exclude non goblinized individuals from taking them - even with TL 9 advancements in ammunitions and small-arm materials, but they can provide extreme amounts of support in a straight up engagement which should not be overlooked by those with the strength to wield them! Just don't go expecting them to magically deal more damage than a normal automatic rifle - pick up an HMG if you want that!

\textbf{GUNS(LMG)(DX-4, or most other Guns at -2)}
\begin{center} 
	\begin{adjustwidth}{-9.5mm}{}
		\scalebox{.93}{
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				Weapon & Damage & Acc & Range & Weight & RoF & Shots & ST & Bulk & Rcl & Cost & LC & Notes \\
				\hline
				Ingram Valiant, 5.56mmCL & 6d pi & 5 & 400/2,200 & 11.96/2.16 & 13 & 100(5) & 11B† & -6 & 2 & 3,500¥/65¥ & 1 & [1,2] \\
				Stoner-Ares M202, 10mmCLR & 8d pi+ & 5 & 550/3,000 & 23.72/4.6 & 12! & 100(5) & 13B† & -7 & 2 & 7,000¥/130¥ & 1 & \\
				\hline
			\end{tabular}
		}
	\end{adjustwidth}
\end{center}

[1] - Laser Sight (UT149).

[2] - Barrel mounted compensator (TS76).

\par\rule{\textwidth}{0.5pt} 

\begin{mdframed}[linewidth=0pt]
\begin{multicols}{2}

\textbf{Ingram Valiant}

A legendary light machine among mercenaries, the Ingram Valiant provides a strong and general purpose use for many battlefield operations. 

It comes stock with a laser sight and barrel mounted compensator, keeping it relatively affordable while maintaining its cheap price while providing the necessities for a modern warfighter.

\textbf{Stoner Ares}

A medium machine gun that backs quite a punch for its relatively light framework. It's a popular secondary weapon for military vehicles, but is often used by trolls and other large methaumans as well.

It comes standard with a 100 round disintegrating belt, however it also can use a 50 round drum magazine: Wt. 22.32/3.2 lb, Shots 50(3).

\end{multicols}
\end{mdframed}

\subsubsection{Machine Guns}

Machine Guns are cover many categories of rifled automatic firearms that are intended to be used for direct sustained fire. Their purposes are often not to simply kill the enemy, but to instead provide enough fire to support other troops and to deter enemy strategies - often through the use of Oportunity Fire (B390), Suppression Fire (B409), or sometimes Spraying Fire (B409). Their major defining trait from Light Machine Guns (LMGs) is their platform - which is usually mounted on vehicles or more permanent mounts (although that is not necessarily case in the Sixth World).

These are almost exclusively mounted on vehicles and large drones, due to their size, but many goblinized individuals can make use of them as well - even if they are not designed for it! If the GM wants some KRIME or similar variants that are intended to be used by individuals, they should consider reducing weight, perhaps a bit of bulk and ST, increasing Rcl, and reducing capacity. Consider looking the Pyramid \#3/37's Blaser and Laser Design, which indicates how the configuration of a weapon affects its Acc, ST, and Bulk!

\textbf{GUNNER(Machine Gun)(DX-4, or other Gunner at -4)}
\begin{center} 
	\begin{adjustwidth}{-10mm}{}
		\scalebox{0.85}{
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				Weapon & Damage & Acc & Range & Weight & RoF & Shots & ST & Bulk & Rcl & Cost & LC & Notes \\
				\hline
				GE Vindicator Minigun, 5.56mmCL & 6d pi & 5 & 400/2,200 & 24.72/4.32 & 50!/100! & 200(5) & 14M & -7 & 2 & 12,000¥/360¥ & 1 & [1, 2] \\
				RPK HMG, 12.7mmCLR & 8dx2 pi+ & 5 & 1,000/7,100 & 43.72/17.05 & 13! & 100(5) & 19M & -8 & 2 & 16,710¥/410¥ & 1 & [3] \\
				\hline
			\end{tabular}
		}
	\end{adjustwidth}
\end{center}

[1] - Integrated Smartgun system. Provides HUD Link (UT149, PY55:8), Targeting Software C3 (UT149), Tiny Computer (UT22). Provides +2 to Guns skill.

[2] - Includes integral D Cell.

[3] - Includes a tripod for non-mounted firing.

\par\rule{\textwidth}{0.5pt} 

\begin{mdframed}[linewidth=0pt]
	\begin{multicols}{2}
		
	\textbf{GE Vindicator Minigun}
	
	One of the most iconic designs for a machine gun, the Vindicator is the great grandchild of popular designs such as the Vulcan. Commonly mounted on large drones and aircraft, it's still not impossible to see enterprising trolls making use of it in person.
	
	The weapon makes use of six belt-fed rotating barrels, electronically timed to fire as each barrel passes by. 
	
	It can optionally be loaded with a 100 round box with an internal belt, commonly used for mobile deployments or by individuals wishing to carry it personally: Wt. 22.56/2.16 lb, Shots 100(5), Cost 10,000¥/340¥	
	
	\textbf{RPK HMG}
	
	A modern contemporary to many old Russian machine gun designs, it is a popular choice for many eastern European and Near Eastern countries, usually as a vehicle support weapon due to its impressive firepower.
	
	It is usually fired mounted, however it is also often used with its included tripod, which reduces its Min ST to 13.
	
\end{multicols}
\end{mdframed}

\subsubsection{Pistols}

Pistols are small round firearms generally designed to be used in one hand. Due to their lack in almost every important metric, they are relegated to back-up and concealable weapons - used in extreme circumstances such as close range fights, smuggling through security, or so on. That being said, some pistols use very powerful rounds that can at least make up for stopping power if not rate of fire!

\textbf{GUNS(Pistol)(DX-4, or most other Guns at -2)}
\begin{center} 
	\begin{adjustwidth}{-10.3mm}{}
		\scalebox{0.88}{
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				Holdout Pistols & Damage & Acc & Range & Weight & RoF & Shots & ST & Bulk & Rcl & Cost & LC & Notes\\
				\hline
				Fichetti Tiffani Needler, 10mmMF & 1d+2 pi- & 1 & 100/1,200 & 1.3/0.09 & 3×3 & 4+1(3) & 8 & -1 & 1 & 159¥/34¥ & 3 & [1]\\
				Streetline Special, .25CLP & 1d+1 pi- & 1 & 120/1,300 & 0.76/0.04 & 3 & 6+1(3) & 7 & -1 & 2 & 183¥/33¥ & 3 & [2] \\
				Walther Palm Pistol, .45CLP & 2d pi+ & 1 & 280/1,100 & 1.09/0.05 & 4 & 2(3i) & 9 & -1 & 2 & 147¥/0.4¥ & 3 & \\
				\hline
				Light Pistols & Damage & Acc & Range & Weight & RoF & Shots & ST & Bulk & Rcl & Cost & LC & Notes\\
				\hline
				Ares Light Fire 70, .380CLP & 2d-1 pi & 2 & 190/1,000 & 1.29/0.19 & 3 & 16+1(3) & 8 & -2 & 2 & 580¥/35¥ & 3 & \\
				Ares Light Fire 75, .380CLP & 2d-1 pi & 2 & 190/1,000 & 1.79/0.19 & 3 & 16+1(3) & 8 & -2 & 2 & 1,300¥/35¥ & 2 & [8] \\
				Beretta 201T, 9mmCLP & 2d+3 pi & 2 & 260/1,200 & 2.65/0.3 & 6 & 21+1(3) & 9 & -2 & 2 & 836¥/36¥ & 3 & [10] \\
				Colt America L36, .45CLP & 2d pi+ & 2 & 290/1,100 & 1.63/0.28 & 3 & 11+1(3) & 10 & -2 & 2 & 687¥/37¥ & 3 & \\
				Fichetti Executive Action, 9mmCLP & 2d+3 pi & 1 & 140/900 & 1.69/0.26 & 9 & 18+1(3) & 9 & -3 & 2 & 762¥/37¥ & 3 & \\
				Fichetti Security 600, 9mmCLP & 2d+3 pi & 2 & 260/1,100 & 2.09/0.43 & 3 & 30+1(3) & 9 & -2 & 2 & 1,024¥/39¥ & 3 & [3,10] \\
				Taurus Omni, .38 Special CLP & 2d+1 pi & 1 & 240/950 & 2.48/0.1 & 3 & 6(3i) & 9 & -2 & 2 & 705¥/0.72¥ & 3 & [6,11] \\
				\hline
				Heavy Pistols & Damage & Acc & Range & Weight & RoF & Shots & ST & Bulk & Rcl & Cost & LC & Notes\\
				\hline
				Ares Predator V, .50 AE CLP & 4d+2 pi+ & 2 & 300/1,500 & 4.35/0.55 & 3 & 15+1(3) & 12 & -4 & 4 & 2,745¥/42¥ & 3 & [7]\\
				Ares Viper Silvergun, 28G MF & 1d+2 pi- & 2 & 105/1,300 & 4.46/1.16 & 9×7 & 30+1(3) & 11 & -4 & 1 & 1,645¥/45¥ & 1 & [12] \\
				Browning Ultra-Power, .40CLP & 2d+2 pi+ & 2 & 310/1,300 & 2.05/0.19 & 3 & 10+1(3) & 8 & -3 & 3 & 855¥/35¥ & 3 & [6] \\
				Colt Government 2066, .45CLP & 2d+1 pi+ & 2 & 290/1,200 & 2.43/0.36 & 3 & 14+1(3) & 10 & -2 & 3 & 860¥/37¥ & 3  &\\
				Remington Roomsweeper, 28G Slug & 4d pi++ & 2 & 115/1,350 & 3.21/.31 & 3 & 8(3) & 11 & -3 & 4 & 436¥/36¥ & 3  & \\
				Remington Roomsweeper, 28G MF & 2d pi- & 2 & 130/1,500 & 3.21/.31 & 3×4 & 8(3) & 11 & -3 & 1 & 436¥/41¥ & 3 &	\\
				Ruger Super Warhawk, .454CLP & 6d pi+ & 2 & 440/2,400 & 3.08/0.2 & 2 & 6(3i) & 12 & -3 & 5 & 788¥/2.4¥ & 3 	&\\
				Taurus Omni, .357CLP  & 3d pi & 1 & 250/1,100 & 2.54/0.11 & 2 & 6(3i) & 10 & -2 & 2 & 705¥/0.96¥ & 3 & [6,11]\\
				\hline
				Machine Pistols & Damage & Acc & Range & Weight & RoF & Shots & ST & Bulk & Rcl & Cost & LC & Notes\\
				\hline
				Ares Crusader II, 9mmCLP & 2d+2 pi & 2 & 260/1,100 & 1.92/0.57 & 3/9\# & 40+1(3) & 9 & -3 & 2 & 2,730¥/70¥ & 2 & [4,7] \\
				Ceska Black Scorpion, .32CLP & 2d pi- & 2 & 170/650 & 3.4/0.35 & 9 & 35+1(3) & 7† & -3* & 2 & 486¥/36¥ & 3 & [3] \\
				Steyr TMP, 9mmCLP & 2d+3 pi & 2 & 260/1,100 & 3.1/.43 & 15 & 30+1(3) & 8† & -2 & 2 & 1,200¥/39¥ & 2 & [6] \\
				\hline
			\end{tabular}
		}
	\end{adjustwidth}
\end{center}

[1] - Programmable Camouflage (UT99)

[2] - Partially made of composite materials; -3 to detect with sensors.

[3] - Detachable/Folding Stock, see Pistol Stock for rules. (HT160)

[4] - Barrel mounted compensator (TS76).

[5] - Design acts as a compensator (TS76).

[6] - Laser Sight (UT149).

[7] - Integrated Smartgun system. Provides HUD Link (UT149, PY55:8), Targeting Software C3 (UT149), Tiny Computer (UT22). Provides +2 to Guns skill.

[8] - Integrated Sound Suppressor, gives -8 to hearing rolls (PY55:11).

[9] - No semi-automatic fire. Minimum RoF 3.

[10] - Detachable stock

[11] - Can switch between .38CLP and .357CLP cylinders.

[12] - Integrated Sound Suppressor, gives -6 to hearing rolls (PY55:11).

\par\rule{\textwidth}{0.5pt} 

\begin{mdframed}[linewidth=0pt]
	\begin{multicols}{2}
		
		\textbf{Fichetti Tifanni Needler}
		
		One of the more subtle palm pistols on the market, the Tifanni Needler is designed to appeal to socialites and debutantes who require the the firepower provided by flechettes while maintaing concealabiltiy.
		
		Beyond its tiny size, it also incorporates Programmable Camouflage (UT99) - commonly used to match it with the user's fashion, but which can easily be used for concealment.
		
		\textbf{Streetine Special}

		A common weapon amongst the dregs of society, this palm pistol is made out of composites and palstics that make it difficult to detect and identify by sensors.
		
		\textbf{Walther Palm Pistol}
		
		One of the smallest pistols on the market, the palm pistol packs a large amount of firepower in a small package. Its major downside is of course its limited number of shots and long reload.
		
		\textbf{Ares Light Fire 70}
		
		One of the most common pistols on the market, the Light Fire 70 is meant for a wide variety of purposes due to its appreciable firepower for its size, ease of use, and of course the Ares name brand.
		
		Ares has a specially designed silencer developed exclusively for the Light Fire 70: -8 to Hearing rolls, 900¥, 0.4 lb.
		
		\textbf{Ares Light Fire 75}
		
		Designed after the Light Fire 70, the Light Fire 75 is marketed towards special operators and is not available through legal channels. It comes standard with the Light Fire silencer integrated internally, allowing for stellar handling while remaining exceptionally stealthy.
		
		\textbf{Beretta 201T}
		
		A common choice for many security progessionals, due to the ubiquitous 9mmCLP round, impressive capacity, and the capability for burst-fire operation without any of the legal hassle that usually comes with it! This unique combination of traits has made it very popular in areas where high caliber or rate of fire pistols are harder to come by.
		
		\textbf{Colt America L36}
		
		A relatively venerable firearm, it manages to hold on due to its great reputation. Its cheap price and easy concealability combined with the ever present cult of the .45 make it a ubiquitous choice and a perfect throwaway weapon.
		
		\textbf{Fichetti Executive Action}
		
		“Manage your danger with Executive Action!” is the latest in a long series of taglines for the Executive Action, its only major selling point is its out-of the box burst-fire capabilites.
		
		\textbf{Fichetti Security 600}
		
		A lighter sidearm marketed towards security forces, its largest selling point is its impressive feeding system that allows for a 30 round magazine without any extension. Even further so, it comes standard with a laser sight and folding stock, allowing for longer range engagement as well.
		
		\textbf{Taurus Omni}
		
		A reliable and rugged revolver, the Taurus is specifically designed to handle multiple types of ammunition flawlessly, allowing one to match the situation as necessary.
		
		\textbf{Ares Predator V}
		
		The newest iteration of the most popular handgun in the world, the Predator V provides absurd firepower for a handgun. Beyond it general improvements over the last generation, it also comes stock with a Smartgun system.
		
		\textbf{Ares Viper Silvergun}
		
		The Silvergun capitalizes on everything that makes flechettes such a terrifying weapon, providing high rate of fire, high capacity, and a built in suppressor all in one.
		
		\textbf{Browning Ultra-Power}
		
		A venerable side arm that provides the major competition for the Ares Predator line, the Ultra-Power provides a cheaper and lower caliber alternative. It comes stock with a laser sight as well.
		
		\textbf{Colt Government 2066}
		
		A modern version of the legendary Colt M1911A1, the Government 2066 incorporates a wide variety of impressive technologies that has earned it a reputation for being exceptionally reliable.
		
		\textbf{Remington Roomsweeper}
		
		More of a sawed-off shotgun with a pistol grip than anything else, the Roomsweeper provides a powerful middle ground between shotguns and pistols, granting high volume of fire with decent concealability.
		
		\textbf{Ruger Super Warhawk}
		
		Called one of the scariest handguns in the world, the Super Warhawk provides absurd firepower that is able to rival rifle calibers. Its one and only purpose is to put such a massive hole in the enemy that they will never get back up. For thrill seekers or nostalgists, Ruger offers cased ammunition purely for the thrill of dumping your spent brass.
		
		\textbf{Ares Crusader II}
		
		One of the most popular machine pistols on the market, the combination of high magazine size, amazing stock attachments, and overall design make it for a powerful firearm. It comes stock with a Smartgun system and a compensator built into the barrel.
		
		\textbf{Ceska Black Scorpion}
		
		Machine pistols don't get much cheaper than this. The Black Scorpion provides a budget and high concealable option for any gunfighter. It comes stock with a folding stock.
		
		\textbf{Steyr TMP}
		
		A futuristic looking machine pistol made almost entirely out of plastics. Its rate of fire allows for serious amounts of lead to be sent down range, but it has difficulty with compensating for that recoil. It comes stock with a laser sight.
		
	\end{multicols}
\end{mdframed}

\subsubsection{Rifles}

Rifles are a diverse set of long arms that make use of rifled barrels to increase accuracy. They fill an extremely wide variety of roles, but are generally classified into Shadowrun's Categories of Rifles/Assault Rifles, Sniper Rifles, and Sporting Rifles.

There's no one role that Rifles excel at, bringing high damage, Accuracy, and Range at the cost of higher Weight, Bulk, and often Rcl. This pushes them towards medium range engagements where targets cannot close the distance quickly alongside targets with good armour and protection. Sniper Rifles in particular are specially crafted to excel at extreme ranges - often over 300 meters, but easily extending up to over a mile - although they can be difficult to properly use in urban environments. An important consideration for any Shadowrunner is how difficult Rifles are to properly conceal and explain away; most are LC 2 or below, which can mean serious trouble if spotted, alongside averaging -4/-5 in Holdout penalties compared to -2/-3 for SMGs and pistols.

\textbf{GUNS(Rifle)(DX-4, or most other Guns at -2)}
\begin{center} 
	\begin{adjustwidth}{-10mm}{}
		\scalebox{0.81}{
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				Rifle & Damage & Acc & Range & Weight & RoF & Shots & ST & Bulk & Rcl & Cost & LC & Notes \\
				\hline
				\hline
				AK-97, 7.62mmCL & 6d+1 pi & 4 & 450/2,400 & 9.3/0.75 & 11 & 38+1(3) & 9† & -5 & 2 & 500¥/48¥ & 2 & \\
				Ares Alpha, 10mmCL & 7d pi+ & 5 & 550/3,000 & 8.05/1.92 & 10 & 42+1(3) & 10† & -4 & 3 & 3,550¥/73¥ & 1 & [1,2,3]\\
				\textit{Underbarrel GL, 40mm} & 1d pi++ & 2 & 75/450 & 2.5/2.4 & 1 & 6(5) & 10 & -1 & 1 & — & 1 & \\
				Colt M23, 5.56mmCL & 5d+3 pi & 4 & 400/2,200 & 6.12/0.6 & 15 & 40+1(3) & 9† & -4 & 2 & 550¥/46¥ & 3 &  \\
				FN HAR, 7mmCL & 6d+1 pi & 4 & 850/4,500 & 8.11/1.04 & 13 & 35+1(3) & 9† & -4 & 2 & 1,400¥/50¥ & 2 & [3,4] \\
				Yamaha Raiden, 10mmCL & 7d+1 pi+ & 5 & 500/2,900 & 9.9/2.74 & 9 & 60+1(3) & 10† & -5 & 3 & 4,000¥/91¥ & 1 & [1,2,3,5,6] \\
				\hline
				Sniper Rifle & Damage & Acc & Range & Weight & RoF & Shots & ST & Bulk & Rcl & Cost & LC & Notes\\
				\hline
				Ares Desert Strike, .300CLR & 9d pi & 6+3 & 1,600/6,600 & 13.18/0.58 & 3 & 14+1(3) & 12B† & -7* & 3 & 6,550¥/46¥ & 2 & [1,8,11] \\
				Ares Desert Strike, 7.62mmCLR & 8d pi & 6+3 & 1,000/4,200 & 13.22/0.62 & 3 & 20+1(3) & 11B† & -6 & 3 & 5,450¥/44¥ & 2 & [1.8,11] \\
				Barrett Model 122, .50CLR & 15d pi+ & 6 & 1,700/6,500 &  27.1/4.5 & 3 & 14+1(3) & 13B†  & -7 & 3 & 17,400¥/70¥ & 1 & [1,2,7] \\
				Cavalier Arms Crockett EBR, 7.62CLR & 8d pi & 5+3 & 1,000/4,200 & 10.62/0.62 &  9 & 20+1(3) & 11B† & -5 & 3 & 4,294¥/44¥ & 1 & [8,10] \\
				Ranger Arms SM-5, .408CLR & 11d+1 pi+ & 6+4 & 1,700/6,500 & 30.7/1.15 & 3 & 15+1(3) & 14B† & -7* & 4 & 13,134¥/65¥  & 1 & [1,6,9,12] \\ 
				Remington 950, 7.62CLR &  8d pi & 6+3 & 1,000/4,200 & 7.9/0.15 & 1 & 5+1(3) & 11† & -5 & 4 & 1,500¥/36¥ & 3 & [1,8] \\
				Ruger 100, .223CL & 5d+3 pi & 5+3 & 500/3,200 & 7/1.1 & 1 & 8+1(3) & 8† & -5 & 2 & 1,413¥/36¥ & 3 & [8]\\
				Terracotta ARMS AM-47, 14.5mmCLR & 9dx2 pi+ & 6+3 & 2,100/8,800 &  55.8/4.4 & 3 & 18+1(3) & 16B† & -8 & 3 &  19,700¥/114¥ & 1 & [1,8,13,14] \\
				\hline
				Sporting Rifle & Damage & Acc & Range & Weight & RoF & Shots & ST & Bulk & Rcl & Cost & LC & Notes\\
				\hline
				M1 Garand, .30-06CLR & 8d+1 pi & 5 & 1,110/4,600 & 8.6/0.44 & 3 & 8(3) & 10† & -5 & 3 & 1,100¥/5¥ & 3 & \\
				%Marlin 3468SS, .45-70 CLR & 
				\hline
			\end{tabular}
		}
	\end{adjustwidth}
\end{center}

[1] - Fine, Accurate.

[2] - Integrated Smartgun system. Provides HUD Link (UT149, PY55:8), Targeting Software C3 (UT149), Tiny Computer (UT22). Provides +2 to Guns skill.

[3] - Design acts as a compensator (TS76).

[4] - Laser Sight (UT149).

[5] - No semi-automatic fire. Minimum RoF 3.

[6] - Integrated Sound Suppressor, gives -6 to hearing rolls (PY55:11).

[7] - Sound Suppressor, gives -6 to hearing rolls (PY55:11).

[8] - Includes Variable Power Scope: x2 (+1), x4 (+2), and x8 (+3).

[9] - Includes Variable Power Scope: x4 (+2), x8 (+3), and x16 (+4).

[10] - Burst Fire, 3 round burst.

[11] - Rugged, +2 HT.

[12] - Fragile, -2 HT.

[13] - Integrated Muzzle Weight (TS76)

[14] - Includes an IFF Interrogator (UT151)

\par\rule{\textwidth}{0.5pt} 


\begin{multicols}{2}
\begin{breakbox}
	
	\textbf{AK-97:}
	
	A modernized version of the classic Kalashnikov rifles, such as the AK-47 and AK-74. Like its predecessors it is known for its legendary reliability, with feats such as being buried for a decade and still being able to fire without issue. For many a modern gunfighter (As well as those without much nuyen to spare), this is an invaluable trait for their firearms.
	
	\textbf{Ares Alpha:}
	
	Possibly one of the most well known weapons in the shadows, the Ares Alpha was originally designed specifically for Ares Firewatch as a powerful option for combating insect spirits. Now it has become one of the best selling weapons the world over, seeing use with military forces around the globe. 
	
	Such a reputation is not undeserved with the Alpha's exceptional capabilities, boasting a great mix of penetration and stopping power, excellent capacity in a compact format, an underslung grenade launcher, Smartgun system, and an ingenious chamber design that functions provides recoil compensation.
	
	Does not come stock with any grenades.
	
	\textbf{Colt M23:}
	
	A cheap an mass produced rifle that is often found in the hands of pirates and the like. While there's nothing outstanding about the rifle itself, it is known as a powerful base for armoursmiths to upgrade from.
	
	\textbf{FN HAR:}
	
	A popular choice with private security and HTR teams, the HAR provides a good middle ground option for any gunfighter. It comes stock with a laser sight and integral compensator.
	
	\textbf{Yamaha Raiden:}
	
	A state of the art assault rifle heavily favoured by Japanese corporations and military forces. It comes stock with integral sound suppressor and smartgun systems, with its ingenious firing mechanism providing the effects of a compensator.  
	
	\textbf{Ares Desert Strike:}
	
	Designed for long-rang shooting in a variety of harsh environments, the Desert Strike was engineering purely with materials and technologies that met rigorous standards for reliability. It comes stock with a x10 Variable-Power Digital Imaging Scope.
	
	While it is originally chambered in .300 CLR, it is often chambered in 7.62 as well depending on the mission.
	
	\textbf{Barrett Model 122:}
	
	An anti-materiel rifle prized for its extreme accuracy just as its predecessors such as the Model 121 were. It keeps with tradition in providing a suppressor and folding bipod, yet not imaging scope - they know you'll just replace it anyways.
	
	\textbf{Cavalier Arms Crockett EBR:}
	
	The Crockett Enhanced Battle Rifle serves a specialized role for a dedicated marksman that provides much of the accuracy that a true sniper rifle has while maintaining many of the aspects that are usually detrimental to said accuracy, such as its burst fire capabilities. It comes stock with a x8 Variable-Power Digital Imaging Scope.
	
	\textbf{Ranger Arms SM-5:}
	
	A legendary assassin's weapon, the Ranger SM-5 is designed to provide the quality and accuracy of a high-grade sniper rifle while simultaneously being able to be broken down into component parts for smuggling. This does come at a cost regardless, as the rifle is quite fragile and need frequent sighting - especially after any rough physical treatment.
	
	Broken down, the rifle is small enough to fit in a standard briefcase alongside its accessories. The process of assembling or disassembling takes around 20 seconds and requires a successful roll against the Armoury (Small Arms) skill - most users take additional time for bonuses and to ensure it is done correctly.
	
	It comes stock with a x20 Variable-Power Digital Imaging Scope and integrated sound suppressor.
	
	\textbf{Remington 950:}
	
	A high powered bolt action hunting rifle. It comes stock with a x8 Variable-Power Digital Imaging Scope.
	
	\textbf{Ruger 100:}
	
	A rather futuristic looking sporting rifle (that is technically still classified as a Sniper Rifle.. for some reason), the Ruger 100 is a favourite for hunters and hobbyists. It comes stock with a x10 Variable-Power Digital Imaging Scope.
	
	\textbf{Terracotta ARMS AM-47:}
	
	An extremely large sniper rifle - which technically meets all requirements as an anti-materiel rifle - intended for use by larger metahumans, the AM-47 will almost assuredly destroy anything its sights are set on. It comes stock with a x10 Variable-Power Digital Imaging Scope, Underbarrel Weight, Bipod, and IFF Interrogator.
	
	\textbf{M1 Garand:}
	
	A modernized version of the classic Garand that maintains the charm of the original without the expense, difficulty, and maintenance.
		
\end{breakbox}
\end{multicols}

\subsubsection{Shotguns}

Shotguns are smoothbore firearms that usually fire multiple projectiles in the form of shotshell, flechette, and so on. There are plenty of options for ammunition in High Tech 162+ and Ultratech 152+ to consider, such as Rifled Slugs and Flechette. 

They excel against unarmored targets, however Multi-Shot projectiles often fall flat against any amount of armour, making them unsuitable against anything better than Armor Clothing - although don't pass up on Random Hit Locations, because it is very easy to incapacitate an opponent when hitting 6 random spots, even if most of their body is protected! While they can use Rifled Slugs to overcome this, they tend to not be as effective as a normal Rifle would be.

It is heavily recommended to use the shotguns created here, due to Ultratech's shotguns being generally \textit{worse} than High Tech's.

\textbf{GUNS(Shotgun)(DX-4, or most other Guns at -2)}
\begin{center} 
	\begin{adjustwidth}{-8mm}{}
		\scalebox{1.0}{
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				Weapon & Damage & Acc & Range & Weight & RoF & Shots & ST & Bulk & Rcl & Cost & LC & Notes \\
				\hline
				Defiance T-250, 12G & 1d+2 pi- & 3 & 45/900 & 6.28/0.33 & 3x9 & 5+1(3i) & 10† & -6 & 1/5 & 347¥/1.75¥ & 3 & [1] \\
				Enfield AS-7, 10G & 2d pi- & 3 & 45/900 & 12/1.6 & 9x9 & 10+1(3) & 12† & -5 & 1/7 & 1,440¥/40¥ & 2 & [1,2] \\
				PJSS Model 55, 12G & 1d+2 pi- & 3 & 45/900 & 8.13/0.13 & 2x9 & 2(3i) & 10† & -6 & 1/4 & 420¥/0.7¥ & 3 & [1]\\
				\hline
			\end{tabular}
		}
	\end{adjustwidth}
\end{center}

[1] - First rcl is for shotshell, second is for slug.

[2] - Laser Sight (UT149).

\par\rule{\textwidth}{0.5pt} 

\begin{mdframed}[linewidth=0pt]
\begin{multicols}{2}
	
	\textbf{Defiance T-250:}
	
	A cheap shotgun commonly used by thugs and goons, it allows for both gas operated semi-auto and pump operated (RoF 2x9) modes of fire. At the GM's discretion the pump operated mode may provide higher Malf numbers.
	
	Additionally, it is available in a short-barreled form (TS69, HT106)\footnote{Primarily uses Tactical Shooting's rules as they're more up to date and conflict somewhat with High Tech.} directly from the point of purchase: Damage 1d+1 pi-, Range 40/800, Wt. 4.78/0.33 lb, Bulk -4, gives +1 to Hearing/Vision rolls to see it due to increased muzzle blast.
	
	\textbf{Enfield AS-7:}
	
	A top line military assault shotgun, the AS-7 provides semi-auto and burst-fire capabilities while maintaining a compact form. It comes stock with a laser sight.
	The AS-7 can also make use an alternative 24 round drum magazine: Wt. 14/3.6, Shots 24+1(3), Cost 1,450¥/50¥
	
	\textbf{PJSS Model 55:}
	
	A double-barreled (Ignore the art) sporting shotgun, renowned among European hunters and trappers for its precision.

\end{multicols}
\end{mdframed}

\subsubsection{Submachine Guns}

Submachine Guns fill a special niche somewhere inbetween Long-arms such as Rifles (Especially Assault Rifles) and Pistols, providing high rates of fire for pistol caliber rounds without being too much larger than a standard pistol. 

They excel in close quarters where their need to stay on the move and get up close are aid by their relatively low bulk and common use of folding stocks. They can struggle against flexible armour without some form of armour piercing - and will almost always be stopped by trauma plates!

\textbf{GUNS(SMG)(DX-4, or most other Guns at -2)}
\begin{center} 
	\begin{adjustwidth}{-8mm}{}
		\scalebox{0.87}{
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				Weapon & Damage & Acc & Range & Weight & RoF & Shots & ST & Bulk & Rcl & Cost & LC & Notes \\
				\hline
				Colt Cobra TZ-120, 9mmCLP & 3d-1 pi & 3 & 260/1,100 & 6.1/0.46 & 14 & 32+1(3) & 8† & -3* & 2 & 1,714¥/39¥ & 3 & [1,2,4] \\
				FN P93 Praetor, 5.7mmCLP & 3d+1(2) pi- & 4 & 160/800 & 5.5/0.36 & 16 & 50+1(5) & 8† & -3 & 1 & 1,826¥/51¥ & 2 & [3,8] \\
				HK-227, .45CLP & 2d+1 pi+ & 3 & 300/1,200 & 5.44/0.72 & 11 & 28+1(3) & 8† & -4* & 2 & 4,442¥/42¥ & 3 & [1,5,6]\\
				Ingram Smartgun X, 9mmCLP & 3d pi & 3 & 260/1,200 & 6.3/0.46 & 19 & 32+1(3) & 8† & -3* & 2 & 2,589¥/39¥ & 3 & [1,3,5,7] \\
				SCK Model 100, 9mmCLP & 3d+1 pi & 3 & 260/1,200 & 3.61/0.43 & 9 & 30+1(3) & 8† & -4* & 2 & 3,200¥/39¥ & 2 & [1,5]  \\
				Uzi IV, 9mmCLP & 3d-1 pi & 3 & 260/1,100 & 7.27/0.34 & 9 & 24+1(3) & 8† & 3* & 2 & 812¥/37¥ & 3 & [1,4,7] \\
				\hline
			\end{tabular}
		}
	\end{adjustwidth}
\end{center}

[1] - Retractable/Folding Stock (HT160).

[2] - Barrel mounted compensator (TS76).

[3] - Design acts as a compensator (TS76).

[4] - Laser Sight (UT149).

[5] - Integrated Smartgun system. Provides HUD Link (UT149, PY55:8), Targeting Software C3 (UT149), Tiny Computer (UT22). Provides +2 to Guns skill.

[6] - Integrated Sound Suppressor, gives -6 to hearing rolls (PY55:11).

[7] - No semi-automatic fire. Minimum RoF 3.

[8] - AP Rounds included in profile.

\par\rule{\textwidth}{0.5pt} 

\begin{mdframed}[linewidth=0pt]
\begin{multicols}{2}
	
	\textbf{Colt Cobra TZ-120:}
	
	A common trid weapon in the hands of security forces thanks to its relatively futuristic design. It comes stock with a laser sight, folding stock, and barrel-mounted compensator.
	
	\textbf{FN P93 Praetor:}

	The standard issue submachine gun for the Corporate Court, it is technically illegal for any individual to own this weapon outside the organization. Its special chamber design acts as a compensator and it also comes stock with a tactical flashlight. 
	
	\textbf{HK-227:}
	
	One of the most popular submachine guns around the world, it works very well against non or lightly-armoured targets. It comes stock with a smartgun system, folding stock, and suppressor - the accessories cost more than the gun itself!
	
	\textbf{Ingram Smartgun X:}
	
	A famous choice for many samurai and trids due to its extremely recognizable silhouette. It comes stock an integrated gas-vent system that acts as a compensatore, an integral suppressor, and a smartgun system.
	
	\textbf{SCK Model 100:}
	
	The Shin Chou Kyogo Model 100 can be found in the hand of almost every Japanese based security force, including the Renraku Red Samurai. It comes stock with a smartgun system and a folding stock.
	
	\textbf{Uzi IV:}
	
	An aging descendant of the famous original. It comes stock with a laser sight and folding stock.
	
\end{multicols}
\end{mdframed}

\subsubsection{Tasers}

Tasers are less than lethal weapons that fire small electrical probes that shock a target into submission. They're ineffective in the face of armour, but can be very powerful in the right situation and against the right target.

\textbf{GUNS(Pistol)(DX-4, or most other Guns at -2)}
\begin{center} 
	\begin{adjustwidth}{-6mm}{}
		\scalebox{1.0}{
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				Weapon & Damage & Acc & Range & Weight & RoF & Shots & ST & Bulk & Rcl & Cost & LC & Notes \\
				\hline
				Defiance EX Shocker & 1d-3 pi- & 0 & 7 & 2/0.1 & 1 & 4(3) & 7 & -2 & 2 & 420¥/20¥ & 4 & [1,2,3] \\
				\textit{follow-up} & HT-6(0.5) aff &&&&&&&&&&& \\
				\hline
				Yamaha Pulsar & 1d-3 pi- & 0 & 20 & 1.1/0.25 & 3 & 4(3) & 7 & -2 & 2 & 368¥/16¥ & 4 & [1] \\
				\textit{follow-up} & HT-4(0.5) aff &&&&&&&&&&& \\
				\hline
			\end{tabular}
		}
	\end{adjustwidth}
\end{center}

[1] - On a failed HT roll victim is stunned while the trigger is depressed and for (20-HT) seconds afterward, and can then roll vs. HT (With the same penalties) to recover.

[2] - Built in biomonitor detects condition of target.

[3] - Can be used as melee Stun Gun, with Reach C and No Parry.

\par\rule{\textwidth}{0.5pt} 

\begin{multicols}{2}
\begin{breakbox}
	
	\textbf{Defiance EX-Shocker:}
	
	The Defiance makes unorthodox use of wired darts, unlike the modern standard of wireless darts, allowing for more powerful shocks at the cost of limited range and rate of fire.
	
	It can also be used in melee in a Stun Gun format.
	
	\textbf{Yamaha Pulsar:}
	
	A classic modern taser, it makes use of wireless darts to reduce cumbersomeness.	
	
\end{breakbox}
\end{multicols}

\subsubsection{Grenade Launchers}

Grenade launchers are a type of Cannon that specializes in the launching of playoads, usually explosive or area effect, of 64mm or less (Most commonly 40mm) at a range further than can be thrown but less than a mortar. They are used for a wide variety of roles, most commonly in urban operations, where they can provide infantry with the ability to clear buildings, provide smoke coverage, attack vehicles and groups, and so on.

They excel as support for many special operations, allowing for the deploy of payloads that help level the often uneven playing fields (e.g. smoke when your team has IR, flashbangs before entering a window, etc). Beyond that, they are positively lethal with the right warheads.

All the launcher below have High Explosive (UT153) warheads, however the Ammunition and Warhead options in High Tech 162+ and Ultratech 152+ are available for other types.

\textbf{GUNS(Grenade Launcher)(DX-4, or most other Guns at -4)}
\begin{center} 
	\begin{adjustwidth}{-9.5mm}{}
		\scalebox{0.96}{
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				Weapon & Damage & Acc & Range & Weight & RoF & Shots & ST & Bulk & Rcl & Cost & LC & Notes \\
				\hline
				Ares Antioch-2, 40mmG & 4d pi++ & 4 & 300/2,000 & 14/2 & 1 & 8(3i) & 10† & -6 & 2 & 3,200¥ & 1 & [1,2]\\
				\textit{follow-up 40mmHE} & 8d cr ex [2d] & — & — & — & — & — & — & — & — & — & — & [3] \\
				ArmTech MGL-12, 25mmG & 4d pi++ & 4 & 360/2,200 & 14/0.72 & 3 & 12+1(3) & 9† & -6 & 2 & 5,000¥ & 1 & [1] \\
				\textit{follow-up, 25mmHE} & 4d cr ex [1d+1] & — & — & — & — & — & — & — & — & — & — & [3] \\
				\hline
			\end{tabular}
		}
	\end{adjustwidth}
\end{center}

[1] - Smartlink allows for wireless detonation of grenades.

[2] - Integrated Smartgun system. Provides HUD Link (UT149, PY55:8), Targeting Software C3 (UT149), Tiny Computer (UT22). Provides +2 to Guns skill.

[3] - See Ammunition and Warhead options in High Tech 162+ and Ultratech 152+.

\par\rule{\textwidth}{0.5pt} 

\begin{mdframed}[linewidth=0pt]
\begin{multicols}{2}
		
	\textbf{Ares Antioch-2:}
	
	An iconic rotary grenade launch firing all sizes of 40mm grenades. It comes stock with an integrated smartgun system.
	
	\textbf{ArmTech MGL-12:}
	
	A bullpup configuration grenade launcher with a loadable magazine, it is able to provide massive ammounts of area control with its semi-auto capabilities.

\end{multicols}
\end{mdframed}

\subsubsection{Missile Launchers}

Missile Launchers cover an extremely wide variety of roles, ranging from Anti-Tank weaponry to even Anti-Infantry, Anti-Building/Materiel, or even area denial. The common thread is that they launch a self-propelled (usually via rocket engine) projectile that contains a payload that is activated at its target.

They come in to broad categories based on their projectiles. Rockets are unguided and head directly in the direction they were shot and are used with the Gunner (Rockets) skill. Missiles are guided projectles that use some form of sensor and computer to guide them towards a specific target, these use the Artillery (Guided Missile) skill to target and fire.

All rockets and missiles in the table are kinetic kill missiles that simply hit the target really fucking fast. See the Ammunition and Warhead options in High Tech 162+ and Ultratech 152+ for other types.

\noindent
\textbf{Gunner (Rockets) (DX-4 or other Gunner at -4) or Artillery (Guided Misile) (IQ-5, or other Artillery at -4)}
\begin{center} 
	\begin{adjustwidth}{-8mm}{}
		\scalebox{0.90}{
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				Weapon & Damage & Acc & Range & Weight & RoF & Shots & ST & Bulk & Rcl & Cost & LC & Notes \\
				\hline
				Aztechnology Striker, 100mm & 6dx30 pi++ & 3 & 2,000/10,000 & 35 & 1 & 1 & 11B† & -4 & 1 & 3,200¥ & 1 & \\
				Mitsubishi Yakusoku MRL, 64mm & 6dx3 pi++ & 3 & 400/3,000 & 40/16 & 2 & 8(5) & 11B† & -8 & 1 & 20,000¥ & 1 & \\
				Onotari Interceptor, 100mm & 6dx30 pi++ & 3 & 2,000/10,000 & 70/50 & 1 & 2(5) & 12B† & -8 & 1 & 16,000¥ & 1 & [1] \\
				\hline
			\end{tabular}
		}
	\end{adjustwidth}
\end{center}

[1] - Integrated Smartgun system. Provides HUD Link (UT149, PY55:8), Targeting Software C3 (UT149), Tiny Computer (UT22). Provides +2 to Guns skill.

\par\rule{\textwidth}{0.5pt} 

\begin{mdframed}[linewidth=0pt]
\begin{multicols}{2}
	
	\textbf{Aztechnology Striker:}
	
	A light disposable rocket launcher, able to deliver a powerful strike before being discard for an unencumbered getaway. 4d burning backblast within a 3 yard radius behind.
	
	\textbf{Mitsubishi Yakusoku MRL:}
	
	A dual-tubed launcher that allow for large capacity and firing rate, while being fairly unwieldy in the process. 2d burning backblast within a 3 yard radius behind.
	
	\textbf{Onotari Interceptor:}
	
	A large military missile launcher with two separate firing barrels chambers. It is unable to fire both at once due to backblast issues. 6d burning backblast within a 4 yard radius behind.

\end{multicols}
\end{mdframed}

\subsection{Ammunition}

Ammunition in Shadowrun is overwhelmingly made of Caseless ammunition and Combustible Cased Telescopic ammunition, allowing for decreased weights and increased magazine sizes. This section contains ammunition for all the weapon provided in this book, however the GM should feel free to add additional types as necessary, which can be accomplished by halving the weight from the modern contemporaries in GURPS High Tech. \textit{Alternatively,} for GMs that wish to maintain the universal ammunition classes from Shadowrun, there are optional generic versions included as well. \newline

\subsubsection{Ammunition Tables}

\begin{tabular}{lll}
	\begin{tabular}{|c|c|c|}
		\hline
		Pistol Caliber & WPS & CPS \\
		\hline
		10mm & 0.021 & 0.24¥ \\
		10mm MF & 0.021 & 0.96¥ \\
		.25 CLP & 0.006 & 0.04¥ \\
		.380 CLP & 0.0105 & 0.08¥ \\
		9mm CLP & 0.013 & 0.12¥ \\
		.38 Special CLP & 0.0165 & 0.12¥ \\
		.50 AE CLP & 0.0335 & 0.4¥ \\
		.40 CLP &  0.0175 & 0.12¥ \\
		.45 CLP &  0.0235 & 0.2¥ \\
		.454 CLP & 0.033 & 0.4¥ \\
		.357 CLP & 0.0175 & 0.16¥ \\
		.32 CLP & 0.009 & 0.04¥ \\
		5.7mm CLP & 0.0065 & 0.16¥ \\
		\hline
	\end{tabular}
	&
	\begin{tabular}{|c|c|c|}
		\hline
		Shotgun Caliber & WPS & CPS \\
		\hline
		28G PC & 0.035 & 0.2¥ \\
		12G PC\footnote{Based on the non-light cased 18.5x70 shotshell} & 0.065 & 0.35¥ \\
		10G PC & 0.075 & 0.65¥ \\
		\hline
		%
		\multicolumn{3}{c}{\vspace{1cm}}\\
		%
		\hline
		Cannon Caliber & WPS & CPS \\
		\hline
		20mm G & 0.35 & 0.35¥ \\
		20mm CL & 0.29 & 5¥ \\
		40mm CL & 1 & 10¥ \\
		\hline
	\end{tabular}
	&
	\begin{tabular}{|c|c|c|}
		\hline
		Rifle Caliber & WPS & CPS \\
		\hline
		7.62mm CL & 0.018 & 0.3¥ \\
		7.62mm CLR\footnote{Descendant of 7.62x51mm NATO.} & 0.028 & 0.4¥ \\
		10mm CL & 0.0415 & 0.75¥ \\
		.223 CL & 0.013 & 0.25¥ \\ 
		5.56mm CL & 0.0135 & 0.25¥ \\
		7mm CL & 0.027 & 0.35¥ \\	
		.300 CLR & .0375 & 0.75¥ \\
		.30-06 CLR & .028 & 0.4¥ \\
		.408 CLR & 0.07 & 1.75¥ \\
		.50 CLR & 0.125 & 2¥ \\
		12.7mm CLR & 0.155 & 3¥ \\
		14.5mm CLR & 0.22 & 3.4¥ \\
		\hline
	\end{tabular}
\end{tabular}

\subsubsection{Warheads and Ammo Types}

Most Warheads and Ammo can simply be found in High Tech 162+ and Ultratech 152+. However, this section details how to either update some rounds to TL9, the custom ammunition here, and/or the Shadowrun setting.

\subsection{Firearm Accessories}
The UT148 Firearm Accessories are \textit{not} included by default on Shadowrun's guns. Usually, none of the equipment is included by default, however GMs may find that diagnostic computers (UT151) should be included by default. If using pre-made equipment from UltraTech (\textit{Not Transhuman Space}), lower cost by 250\$.

Players should also look into the \hyperref[3/55]{Pyramid \#3/55 section}, which covers many ideas, updates, and improvements to basic Ultratech equipment and accessories.

\subsubsection{Smartgun}\label{smartgun}
1,900¥, 0.12 lb

Smartguns are a technological wonder for the modern gunfighter. A composite of multiple sensors and software suites, including cameras, laser rangefinders, material sensors, and more - they are able to maintain many of the the difficult information in a gunfight alongside calculating optimal firing solutions for the user.

Smartguns themselves are made up of a Dedicated Tiny Computer (25¥, 0.01lb, UT22) running a HUD Link (250¥, UT149, PY:55 8), Targeting Software C3 (500¥, UT149), and Target Tracking C3 (1000¥, UT149), a Diagnostic Computer (25¥, 0.01 lb, UT151), and multi-spectral laser rangefinder (100¥, 0.1 lb TS 27) all in one tiny package. These provide a slew of bonuses and options for a gunfighter. 

The Dedicated Tiny Computer - equipped with a cable jack (UT 42), micro radio communicator (UT 44), and mini-camera (UT 51\footnote{While referenced in the Datapad entry, this doesn't technically exist. Either way it's simply a negligible weight, cost, and powered camera.}) is hardwired to run its programs, which provide a total of +2 bonus to all Guns and Gunner skill to use the firearm alongside the ability to track up to 100 targets or objects of note. Additionally, the HUD's improvements to situational awareness provide +1 to skill rolls when reacting to information quickly is important (UT 24) alongside removing up to -3 in darkness penalties with Sighted or Aimed Shooting (TS 13-14) with it due to its illuminated markers (PY:55 8) - for which it \textit{always is} when using a HUD link, alongside other bonuses (PY:55 8). PY:55 p8 also covers how to use this to shoot around corners.

The firearm's \hyperref[diagnostic_computer]{Diagnostic Computer (25¥, 0.01 lb)} provides a number of useful functions when combined with the HUD Link as described below.

Lastly, the multispectral laser rangefinder can provide the Rangefinder Bonus (TS 27) as a Free Action when combined with a HUD Link and Targeting Software, giving a +3 bonus to Acc.

When combined with Smartgun Cyberware, this can instead run Complexity 4 Targeting Software, giving an additional +1 to Guns and Gunner skill. Increased costs are incorporated into the Cyberware itself, so simply buy them both together. While it is easily possible for a gunfighter to buy a Fast Tiny Computer and load such software into his normal gun without getting cyberware, it's in the spirit of the setting for the GM to disallow such things. 

\subsubsection{Compensator}
125¥, 0.1/0.25/0.35 lb LC 3

Compensators take a variety of forms in the Sixth World, usually one of either barrel attachement Gas Venting Systems or as built in designs for certain firearms. Compensator rules are covered in Tactical Shooting p76. A GM could reasonably allow certain weapons to be retrofitted with Compensator-like Gas Venting designs - as seen in certain firearms such as the Ares Alpha. This should probably at a minimum be costed as purchasing Good quality equipment, but is ultimately left up to GM.

\subsubsection{Diagnostic Computer}\label{diagnostic_computer}
25¥, 0.01 lb.\footnote{Priced and weighted as a Dedicated Tiny Computer with free basic software.} LC 4

A common addition to many firearms, especially when included in smartgun packages, the Diagnostic Computer both helps to maintain the firearm itself while also providing an array of useful gunfighting information (PY55:7). 

In addition to its +1 bonus to all rolls to diagnose and repair damage and malfunctions (including Immediate action rolls), it also is able to alert the user to low/empty magazines - or display the amount on a HUD link (TS 20). Additionally, the types of ammunition can be easily tracked, which can make mixing ammunition (TS 31) slightly less stupid. In hazardous environments that would readily affect the malfunction of the gun, the computer can alert the user of the issues; this is not a replacement for genuine hazardous environment warning equipment though, as it only indirectly warns users of such things (e.g. receiving a warning for lubricant malfunctions due to the pressure in a room suddenly dropping). Do note that displays, HUD Links, and terminals (UT 23-24, 149, PY:55 8)are not included by default, requiring a cable to retrieve information.

\subsubsection{Folding Stock}
100¥, 0.5 lb LC 3

Folding Stocks are common additions to pistols (for additional accuracy and control) and to rifles (for flexibility and handling). Adding folding stocks to firearms is covered under High Tech 160.

\subsubsection{Imaging Scope}
Var. ¥, Var. lb LC 3

Imaging Scopes cover a wide range of scopes and can include a ton of differing functionalities. Many high-tech solutions can be represented with the Compact Targeting Scope or the Enhanced Targeting Scope - however, for scopes that use differing magnifications, vision advantages, or form factors, see the rules proposed below. General rules and equipment are found on B412, HT47 and 155, UT 60 and UT149, with additional rules on TS26 - although an often missed one is the additional Bulk for scopes over 4x magnification. None of the scopes below include any HUDs, digital cameras (beyond what's necessary to operate the sensors), or rangefinders. When building an optic, it may be preferrable to have a lower magnification for a larger housing, such as x4 magnification in a camera housing (a 3 lb. weight); in such a case, use the cost of the actual Accuracy, but simply use the larger weight (and all effects such as higher HP and size). Additionally, many of them do not perfectly align with their contemporaries in Ultratech, which the GM should feel free to alter to their whims.

All scopes in the tables above are simply Digital Variable-Power Optical Scopes, providing no special Vision Advantages.

\textbf{Optical Scopes}

Many awakened need to make use of entirely natural lines of sight in order to target their spells and abilities, which require low-tech optical scopes that simple use lenses to focus and magnify light. For simply optical ones, use the rules on High-Tech 155-156. Such scopes can be digital or optical at no extra cost, with digital allowing benefits such as sharing LOS with teammates and so on.

\textbf{Night Vision}
Night Vision optics give a level of Night Vision equal to 7 + Their Acc bonus (Maximum of 9).  Note that early Night Vision does not allow for Awakened to cast spells, due to it converting the original light to electrical signals that are them intesified and displayed on a phosphor screen - and modern ones are digital, which is right out!

Weight depends on Acc: +0 (0.1 lb.), +1 (0.3 lb.), +2 (0.6 lb.), +3 (1.3 lb.), +4 (3 lb.), +5 (7 lb.), +6 (15 lb.)

500¥ per +1 Acc. LC 4. -1 Bulk for Acc above +2.

\textbf{Infrared}
An easy option for Infrared Optics is the Compact Targeting Scope, which provides Infravision and x4 Magnification (+2 Acc), otherwise use these rules:

Weight depends on Acc: +0 (0.1 lb.), +1 (0.3 lb.), +2 (0.6 lb.), +3 (1.3 lb.), +4 (3 lb.), +5 (7 lb.), +6 (15 lb.)

500¥ per +1 Acc. LC 4. -1 Bulk for Acc above +2.

\textbf{Hyperspectral}
An easy option for Hyperspectral Optics is the Enhanced Targeting Scope, which provides Hyperspectral, x8 Magnification (+3 Acc), and - I am arbitrarily ruling based off its description and cost - a multi-mode Rangefinder, otherwise use these rules:

Weight depends on Acc: +0 (0.1 lb.), +1 (0.3 lb.), +2 (0.6 lb.), +3 (1.3 lb.), +4 (3 lb.), +5 (7 lb.), +6 (15 lb.)

2,000¥ per +1 Acc. LC 4. -1 Bulk for Acc above +2.

\subsubsection{Laser Sight}\label{laser_sight}
75¥, 0.05 lb LC 3

A Muli-spectral Laser Sight UT (149) serves as the lower-tech solution for any firearm. It provides +1 to skill when used out to the 1/2D if you can see it, but also provides a +1 to dodge it if \textit{your opponent} can see it! For most lasers and ranges their beam-width gives a SM of -13 to -10 alongside bonuses for brightness and contrasting (up to the GM, a good heuristic is a bonuse equal to the darkness penalty +1, with a bonus similar to camouflage bonuses and penalties (HT 76)).

\subsubsection{Suppressor}
100-800¥, 0.5/1/2 lb LC 2-3

Covered under High Tech p158-159, Tactical Shooting p70-71 and PY:55 p11, suppressors are heavily enhanced for TL 9. They provide Hearing penalties from -1 to -8 - with a standard of -6 (Which is present on all firearms in the tables) - and cost 100¥ per -1 of Hearing penalties. Weights above are for pistols, rifles (and similar sized weapons), and for oversized guns respectively. This can be effective enough to actually approach Trid noise levels, such as a Rifle lowering from 140 dB to 80 dB or even 60dB - or about as loud as reloading the damn thing! The GM may - rightfully - say that the level cannot go lower than 60dB, representing the firearm and action itself and complete neutralization of the crack and expanding gasses.

\subsubsection{Muzzle Weight}
100¥, 0.1-0.5lb LC 3

A low-tech alternative to Compensators/Gas Vents, a finely tuned weight can help to reduce recoil. Rules can be found on Tactical Shooting p76.

\subsection{Additional Accessories}

\subsubsection{Concealable Holster}
125¥, 1 lb. LC 4.

Rules for holsters built to be concealed are found on High-Tech p154.

\subsubsection{Quick-Draw Holster}
500¥, 3lbs. LC 4.

Rules for holsters that are built for speed can be found on High-Tech p154.

\subsubsection{Slings}
Var ¥, Var lbs. LC 4

Rules for a variety of slings can be found on High-Tech p154.

\subsection{Firearm Noise}

Pyramid \#3/55 - Military Sci-Fi, Tactical Shooting: Tomorrow notes how Electronic Firing lowers the volume for firearms and changes the table found on High Tech 158, as noted below. Additionally, the Ares Gauss Thunderstruck also benefits from these rules (Being a gauss rifle after all) and additionally can make use of the silenced mode to lower it further.

\subsubsection{Hearing Distance Table}
Sound: Weapon sound in question (other sounds included for comparison).\\
dB(A): Decibel range at muzzle, weighted for human hearing.\\
Range: Distance (in yards or miles) at which sound is audible on an unmodified Hearing roll.\\
\begin{center} 
	\begin{adjustwidth}{-6mm}{}
		\scalebox{1.0}{
			\begin{tabular}{|c|c|c|c|}
				\hline
				Sounds & Range dB(A) & Range (yards) & (miles) \\
				\hline
				Leaves rustling, stalking person & 40 & 0.25 & - \\
				Quiet conversation, walking person & 50 & 0.5 & - \\
				Conversation, cocking or reloading a firearms, attaching a bayonet & 60 & 1 & - \\
				Light traffic & 70 & 2 & - \\
				Bow, loud conversation, noisy office & 80 & 4 & - \\
				Crossbow, shouting, gasoline engine & 90 & 8 & - \\
				Air Gun, revving gas engine & 100 & 16 & - \\
				Loud Clapping, diesel engine, auto horn, motorcycle & 110 & 32 & - \\
				Very light pistol or rifle (.22), chainsaw, oxygen torch & 120 & 64 & - \\
				Light Pistol (.32 CLP, .380 CLP), grenade launcher & 130 & 128 & - \\
				Heavy Pistol (9mm CLP, .45 CLP), SMG, rifle, shotgun & 140 & 256 & 0.15 \\
				Magnum rifle (.300 CLR, .600 CLR), HMG & 150 & 512 & 0.3 \\
				Artillery, Assault Cannon, Stun grenade & 160 & 1024 & 0.6 \\
				Tank gun, Panther XXL, small explosion & 170 & 2048 & 1.2 \\
				Large explosion & 180 & 4096 & 2.3 \\
				\hline
			\end{tabular}
		}
	\end{adjustwidth}
\end{center}

\subsection{Drugs and BTLs}

The Sixth world has a diverse selection of drugs for every junkie to get their high from. In addition to the drugs provided in Biotech, Basic Set, High Tech, and Ultratech, below are a number of Shadowrun classics to indulge in - and of course remember that it's the winners who use drugs. Importantly, because Per and Will are separate from IQ, many drugs that positively or negatively affected IQ need rulings on whether they also influence those secondary stats. In general, this is best left to the GM as to whether it also affects them, but in general the answer should be no unless there's a clear correlation; certain drugs should have additional options available for Per and Will versions, such as Adders (BT155).

Rules for Drug Withdrawal can be found on Basic Set 441. These rules require either a physiological or psychological dependency, as such all drugs that are both have a primary method notated; the GM should feel free to require a character to use the worse method - or to require them to succeed on both, although perhaps with a +1 Bonus to their rolls.

\subsubsection{Bliss}
\begin{flushleft}
	3¥ per dose, LC 3. 
	Dependency: Both (Physiological)
\end{flushleft}

A tranquilizing narcotic opiate, similar to Morphine. If taken orally, there is a 20 minute delay; if injected there is no delay. Roll versus HT-4 to resist. On failure, the user acquires High Pain Threshold, Unfazeable, and Laziness alongside experiencing the Euphoria condition (B428). Lasts a number of hours equal to margin of failure. See Narcotic Painkillers, Biotech p149.

\subsubsection{Cereprax}
\begin{flushleft}
	720¥ per dose, LC 1. 
	Dependency: Both (Psychological)
\end{flushleft}

A potent nootropic that is able to boost neurological capabilities immensely, at the expense of extreme metabolic function and fatigue crashes. It is usually taken orally, in which case there is a 5 minute delay. Roll versus HT-3 to resist. On failure, the user acquires +2 IQ, +2 Per, and the Eidetic Memory quality, lasting for a number of hours equal to margin of failure. When the drug wears off, the user suffers for severe migraines and fatigue. They lose 2d6 FP and gain the Chronic Pain, Severe Disadvantage in the form of horrible migraines; the user must roll against a FoA 15 immediately, suffering the migraines for a 4 hour period if the roll passes.

Overdoses from Cereprax can happen easily and are particularly dangerous. Following the Overdose rules on B441, taking multiple doses provides a -2 to the resistance roll per dose past the first - however any critical failure is an Overdose. For Cereprax, this causes permanent brain damage and bleeding, see the poison rules below:

\textbf{Cereprax Overdose} An overdose on Cereprax causes unconsciousness for hours equal to margin of failure. Additionally, it functions as a poison, with an HT-7\footnote{Cereprax provides a -4 penalty to resist its overdoses, meaning the poison resistance roll is its usual resistance roll with a -4.} to resist. It inflicts 1 toxic damage, repeating at 15 minute intervals for 24 cycles. If the user loses $\times$1/2, $\times$1, and $\times$2 HP they suffer increasingly severe brain damage; the gain [-5], [-20], and [-35] points in negative/lost mental qualities and attributes - most often lowered Per and IQ, but this can also mean losing advantages related to logical and spatial thinking such as Eidetic Memory. Additionally, users that haev suffered any brain damage also suffer seizures until conscious again.

\subsubsection{Cram}
\begin{flushleft}
	10¥/20¥ per dose, LC 3. 
	Dependency: Psychological
\end{flushleft}

Cram is a popular stimulant that affects the user's reaction speed and impulses as opposed to simply boosting attentivity and reducing need for sleep. It can be taken orally (10¥ pill), in which case there is a 20 minute delay, or via inhalation (20¥ popper), which has a 10 minute delay. Roll HT-3 to resist. On a failure, the user gains +0.50 to their Basic Speed (this does not affect Basic Move), lasting for hours equal to Margin of Failure. Additionally, they gain the Impulsiveness (SC 12) and Odious Personal Habit, -1 (Fidgeting and Jittery) Negative Disadvantages for the duration.

\subsubsection{Deepweed}


\subsubsection{Jazz}
\begin{flushleft}
	96¥ per dose, LC 3. 
	Dependency: Both (Physiological)
\end{flushleft}

Jazz is a very potent stimulant, often used to equal the playing field between mundanes and street samurai or adepts. It can be taken via inhalation (through a single use popper most commonly), with no delay. Roll HT-3 to resist. On a failure, the user gains +1.25 to their Basic Speed (this does not affect Basic Move), lasting for a number of minutes equal to 5 times the margin of failure. Additionally, they gain the Odious Personal Habit, -1 (Hyperactive) Negative Disadvantage for the duration, and when the drug is finished the crash, suffering the Chronic Depression (SC 12) Negative Disadvantage for a number of minutes equal to the original duration.

\subsubsection{Kamikaze}
\begin{flushleft}
	128¥ per dose, LC 3. 
	Dependency: Physiological
\end{flushleft}

Kamikaze is a tailored combat stimulant - and a very potent on at that. It can be taken via Inhalation, with no delay. Roll HT-4 to resist. On a failure, the user gains +1 DX (With no Basic Speed), +4 ST (With no HP), and +1.0 Basic Speed (With no Basic Move), alongside providing a +3 to all HT rolls dealing with pain - making them into a veritable killing machine for a number of minutes equal to 5 $\times$ Margin of Failure. However, they also gain the Berserk (SC 12), Megalomania, and On the Edge (SC 12) Negative Qualities, turning them into near-crazed madmen, filled with thoughts of imperviousness and invulnerability. Once the drug is finished, they crash hard, losing 2d+1 FP and suffer the Chronic Pain, Mild Disadvantage in the form of muscle pain, shortness of breath, and sluggish movement; the user must roll against a FoA 15 immediately, suffering the migraines for a 2 hour period if the roll passes. 

Kamikaze can be dangerous in higher doses, even before Overdosing, causing hallucinations and/or anxiety when taking multiple doses and can cause overdosing similarly to Heroin. Overdosing is as Heroin.

\subsubsection{K-10 (Blood of Kali)}
\begin{flushleft}
	1,150¥ per dose, LC 1. 
	Dependency: Both (Physiological)
\end{flushleft}

Kamikaze Grade 10, colloquially known as K-10 or the Blood of Kali, is an experimental combat drug known for getting its user and everything near them killed. Hacked from an experimental pharmaceutical lab's database and leaked to the streets, it's become infamous for its effects. It can only be taken via injection, with no delay. Roll HT-6 to resist. On a failure, the user gains +2 DX (With no Basic Speed), \textit{+8 ST} (With no HP), +1.25 Basic Speed (With no Basic Move), and +1 Will, alongside the High Pain Tolerance Advantage, all for a number of minutes equal to 5 $\times$ Margin of Failure. This all comes at some steep costs, affecting the user with the Berserk (\textit{No SC}) for the duration alongside causing 6d FP Loss after the drug wears off alongside a tendency to leave the user \textit{permanently} berserk. Any resistance roll that fails for 5 or more means the user is \textit{permanently berserk} and cannot come back without some sort of medical miracle.

\subsubsection{Long Haul}
\begin{flushleft}
	58¥ per dose, LC 4.
\end{flushleft}

A powerful stimulant made from a combination of synthesized hormones and brain-regulating chemicals that can keep the user awake for days on end. The drug is taken via injection, with a delay of 10 minutes. Roll HT-4 to resist. Failure gives the user Doesn't Sleep for 1d6 \textit{days}. After this time is up, the fatigue comes crashing back down upon him, causing him to take 17 fatigue and to sleep for 28 hours (unless they are miraculously able to make the continuous Will rolls for Missed Sleep).

\subsubsection{Nitro}
\begin{flushleft}
	64¥ per dose, LC 3.
	Dependency: Both (Physiological)
\end{flushleft}

A dangerous combination of stimulants favored by troll gangers. Taken via inhalation, it has a delay of 10 seconds. Roll HT-4 to resist; failure gives the user +2 ST (With no HP), +1 Will, Acute Vision and Hearing 2, and the High Pain Tolerance advantage for a number of minute equal to the Margin of Failure times 5. However, while under the effects, the user suffers from the Short Attention Span (SC 12) and Odious Personal Habit, -1 (Talkative) disadvantages. After the effects wear off, they lose 3d6 FP as they crash hard.

\subsubsection{Novacoke}
\begin{flushleft}
	64¥ per dose, LC 3.
	Dependency: Both (Psychological)
\end{flushleft}

A powerful sixth world stimulant  derived from coca plants, it is a social drug designed to boost user's 'charisma' through increased energy, confidence, efficacy of mirror neurons and social processing centers, and so on. It can be taken via injection (12¥), with no delay, or via Inhalation (24¥), with a delay of 1 minute. Roll versus HT-4 to resist. Failure provides the user with Charisma 2 for a number of hours equal to their Margin of Failure. However, the crash afterwards is brutal, lowering the user's Will by 2 alongside providing -30 points in social disadvantages or lost social advantages for an equal number of hours. The GM should choose what these are, but they should reflect the burnout, depression, and compulsive behaviours that often occur after the drug wears off through disadvantages such as Low Empathy [-20], Compulsive Behaviours [-5* to -15*], Odious Personal Habits [-5 per level], Bad Temper [-10*], Bully [-10*], Callous [-5], Chronic Depression [-15], and Impulsiveness [-10*].

\subsubsection{Psyche}
\begin{flushleft}
	160¥ per dose, LC 4.
	Dependency: Psychological
\end{flushleft}

A designer stimulant and nootropic, Psyche provide a wide and general boost to a user's intellectual capability. It can be taken through Ingestion, with a 10 minute delay. Roll versus HT-4 to resist. Failure gives the user +1 IQ for a number of hours equal to Margin of Failure. Additionally, the user becomes obsessive and compulsive during that period, suffering from a Short Term Obsession (SC 9) to the point that it becomes an Odious Personal Habit, -1. Additionally, the gain the Attentive (B163), Methodical (PU:6 19), and Perfectionist (PU:6 20) quirks, showcasing their highly increased focus and absorption in to detail. For Awakened and Emerged, this drug is even more valuable, allowing them to sustain additional spells at the same time - at the cost of large decreases in logical capabilities due to the mental tax. Calculate the point cost to gain another sustaining slot as if you were to normally purchase one (Most often, this is simply the full cost of your most expensive spell or similar advantage). For every 20 points (rounded up), the user is able to sustain another effect at the cost of a cumulative -1 IQ, Per, and DX penalty (derived stats are unaffected) while they are sustaining (e.g. if your most expensive spell is Healing at Magic 3 [57], 57/20 is 2.85, meaning you take an additional -3 to IQ, Per, and DX when sustaining).

\subsubsection{Zen}
\begin{flushleft}
	10¥ per dose, LC 3.
	Dependency: Psychological
\end{flushleft}

A popular short-term psychedelic hallucinogen. It is taken via inhalation, with a speed of 5 minutes. Roll versus HT-3 to resist. Failure gives the users the Hallucinations condition (B428) for a number of minutes equal to 5 times their Margin of Failure. Many users still engage in the less potent, but longer lasting hallucinogenics of the past (B440).

\subsection{Drug Addiction}

GURPS fundamentally lacks any rules covering the process of becoming addicted to a substance. \textcolor{blue}{\href{http://forums.sjgames.com/showpost.php?p=186043&postcount=3}{Kromm has covered the reasons for this before}}, which can simply be summed up as it being too complex a system to neatly wrap into any semblance of rules. Nevertheless, it is necessary for some set of objective metrics for the setting, due to Shadowrun's pervasive and encouraged substance abuse, all in the sake of chasing the Punk in Cyberpunk.

The primary method for Addiction is to simply have the GM call for HT or Will rolls (depending on the dependency type) whenever the players partakes in too many drugs, with a failure indicating they have gained the Addiction negative quality. This is short and simple, allowing for the GM to drive the costs of substance abuse at dramatic moments - but it lacks in any sense of objective fairness or risk-management for the players!

Alternatively, a more complex system the aims to capture some of the complexities is as follows:

Whenever you take a substance, you must make an immediate addiction test with the modifiers listed below. Success means that you have staved off the spiral and are good until you indulge again. Failure means that you are now in danger of developing a dependency on the substance, and must track the following rules continued below.

\textcolor{NavyBlue}{\textit{Modifiers: A flat +4 task difficulty bonus; A penalty equal to the Addiction Rating for the substance (see below); A -1 to -4 penalty, for any mental disadvantages that reduce self-control, such as Impulsiveness and Compulsive Behaviour, (even if they aren't drug related), corresponding to SC 15 through 6 respectively (e.g. SC 12 gives -2); A +1 to +4 bonus, for any mental advantage or disadvantages that increase self-control or oppose addiction, such as Disciplines of Faith and True Faith (For certain beliefs)}}

When a user fails their initial test, they are in danger of succumbing to addiction. They must make a series of daily rolls (similarly to the Withdrawal system). Roll against HT or Will (For Physiological or Psychological respectively), with all the same modifers as above alongside an additional +1. Succeeding on these tests puts them a day closer to shaking this off and grants a cumulative +1 bonus to all further tests; if the user's resistance roll ever goes above 18 they are home free and are no longer at risk of addiction. If they fail, they or their body give in and gain the Addiction quality for their substance.

This makes it relatively safe for anyone to use AR -0 and -1 drugs, a little risky for anyone under HT 11 to use AR -2 drugs, risky for anyone under HT 11 to use AR -3 drugs, risky for anyone under HT 12 to use AR -4 and -5 drugs, and risky for anyone under HT 13 to use AR -6 drugs. Mental traits and circumstance can shift this either way, but having a personality disposed toward drugs can be very impactful, increasing your risk by one or two categories. It also addresses the issue present in base Shadowrun where users would simply wait out the Addiction timer or alternatively Edge their roll during downtime to prevent any consequences; now the most impactful roll is during that initial use period, likely on a mission, with the incremental slip coming later.

\textbf{Addiction Ratings}

The numbers here were derived from the Addiction Table in Shadowrun's Core Rulebook p414; see \hyperref[behind_the_screen]{the Behind the Screen section} for further details.

\begin{center}
\begin{tabular}{ll}
	\begin{tabular}{|c|c|}
		\hline
		Substance & Addiction Rating \\
		\hline
		Alcohol & -1 \\
		Bliss & -3 \\
		Cereprax & -5 \\
		Cram & -2 \\
		Jazz & -5 \\
		Kamikaze & -5 \\
		K-10 & -6 \\
		Long Haul & -0 \\ 
		Nitro & -5 \\
		Novacoke & -3 \\
		Psyche & -3 \\
		Soykaf & -1 \\
		Zen & -0 \\
		\hline
	\end{tabular}
	&
	\begin{tabular}{|c|c|}
		\hline
		Substance & Addiction Rating \\
		\hline
		BTL, Dreamchip & -2 \\
		BTL, Moodchip & -3 \\
		BTL, Personafix & -3 \\
		BTL, Tripchip & -5 \\
		Hot-Sim Simsense & -0 \\
		Legal-Strength Simsense & -0 \\
		Skillwires & -2 \\
		Focus Addiction & -Force/2 \\
		Essence Drain & -Magic/2 \\
		\hline
	\end{tabular}
\end{tabular}
\end{center}

\subsection{Chemicals and Toxins}

Chemicals or Toxins are a great way to commit war crimes and also to take down many an unsuspecting opponent. Don't forget when using Aerosol to refer to the Biochemical Aerosol warhead in UT153 for the amount of doses necessary by size (e.g. Hand grenades require 150 doses).

\subsubsection{CS/Tear Gas}
\begin{flushleft}
	Var¥ per dose, LC 3. 
\end{flushleft}

A contact and inhalation based toxin that causes irritation to the lungs, eyes, so on. Can be found on HT 171, 180, 192, and 193, alongside some extra dirty tricks beyond what Shadowrun had.

\subsubsection{Dimethyl Sulfoxide (DMSO)}
\begin{flushleft}
	1¥ per dose, LC 3. 
\end{flushleft}

Found on Biotech p157, this chemicals is not a drug itself, but it can penetrate the skin (Contact Agent) and carry other drugs into the body.

\subsubsection{Gamma-Scopolamine}
\begin{flushleft}
	20¥ per dose, LC 1. 
\end{flushleft}

A nasty drug derived from night-shade and the grandchild of many paralyzants and truth-serums (HT 227, BT 157). It is administered via injection, with no delay. Roll versus HT-3 to resist every 30 minutes for 4 cycles. Failure means paralysis (B428) until the cycles have finished. As well, if any rolls are failed, the victim suffer -2 to Will throughout the duration and for 1 hour afterwards.

\subsubsection{Laés}
\begin{flushleft}
	960¥/1,920¥ per dose, LC 1.
\end{flushleft}

Laes is a powerful poison and chemical developed by the government of Tir Tairngire, able to retroactively erase short term memories and knock individuals unconscious. It can be administered orally, with a delay of 5 minutes (960¥), injected, with no delay (960¥), or given via inhalation, with a delay of 5 minutes (1,920¥). Roll HT-5 to resist every second for 12 cycles; each failure costs 1 FP. If this deals FP over 1/2, the victim loses the last [25-HT] hours memory. These memories are chemically lost and cannot be recovered with technology or magic.

\subsubsection{Narcojet}
\begin{flushleft}
	50¥ per dose, LC 2. 
\end{flushleft}

A common tranquilizer that combines the speed of Sleep Poison (UT 161) and the potency of Chloral Hydrate and Flunitrazepam (BT 152). It is administered via injection, with no delay. Roll HT-5 to resist. Failure causes drowsy (B428) for 5 seconds before falling into a deep sleep that they cannot wake from for (8 - HT/2) hours. Success also results in sleep, but the victim remains drowsy for 1 minute and then falls asleep for 2 hours less. Critical success allows the victim to remain awake, however they remain drowsy throughout the duration as if they had succeeded.

\subsubsection{Nausea Gas}

See CS/Tear Gas above, Nausea Gas is included in that section.

\subsubsection{Neuro-Stun}
	
See Sleep Gas (UT 160).

\subsubsection{Pepperpunch}

See Pepper Spray (HT 180). Cost, Radius, and so on are as for Tear Gas warheads (HT 171).

\subsubsection{Seven-7}
\begin{flushleft}
	20¥ per dose, LC 0. 
\end{flushleft}

A fast acting, colourless, odorless gas designed to lethally bypass many chemical protections. It has a contact or inhalation vector, with a 3 second delay. Roll HT-4 to resist every second for  6 cycles. Failure causes 1d tox damage, with a loss of 1/2 HP causing nausea (B428). For a similar, but more potent version see Nerve Gas, Lethal (UT160).

\subsection{Drones}\label{drones}

Drones are semi-autonomous electrical robots that can provide a wide variety of utility, ranging from combat, to scouting, to repair work, and more.

\subsubsection{Drone Meta-Trait}
\begin{flushright}
	22 Points
\end{flushright}

All drones have a number of traits that are in common with on another. This Meta-Trait combines them all in order to keep the statblocks reasonably concise to read. The drone meta-trait deals purely with the body of the drone, and as such only include physical traits and attributes - anything that a pilot program specifies overrides this template!

Notably, drone bodies indicate their DX as a bonus instead of a flat trait. This is because digital minds / riggers use their own DX, modified by the drone body's (e.g. a rigger with DX 12 jumping into a Doberman acts as if he had DX 14).

All drones have \hyperref[firewall]{Firewalls} that come with their models. For drones SM-5 and smaller, this is usually a Complexity 3 Inferior Firewall; for up to SM+1, this is usually a Complexity 4 Standard Firewall; for up to SM+4, this is usually a Complexity 5 Standard Firewall; higher SM drones are usually the same, however it is possible for drones SM+8 to be Complexity 6, for drones up to SM+12 to be Complexity 7, and for drones up to SM+16 to be Complexity 8, although once you're past 4 it's more of a server than a drone. Some drones will instead opt for Superior Firewalls instead of higher Complexities.

It's also important to note some advantages and disadvantages that one might mistake drones for having. Many drones will likely make use of singular cameras, which might imply the One Eye [-15] disadvantage. However, many cameras can make use of varied detection and processing tactics that practically remove any loss of depth perception. Many Injury Tolerances may seem immediately likely, such as No Vitals or No Brain. However, these are just different object in a drone, notably the brain usually being the CPU.

\textbf{Advantages:} 
Absolute Direction (Requires Signal, -20\%; Mundane Countermeasures, -10\%) [4]; Doesn't Sleep [20]; High Pain Threshold [10]; Injury Tolerance (No Blood, No Neck, Unliving) [30]; Injury Tolerance (Independant Body Parts) (Reattachment Only, -50\%; Nuisance Effect, Reattachment requires maintenance, -5\%) [16]; Resistant (Immunity, Metabolic Hazards) [30]; Telecommunication, Radio (Secure, +20\%; Sensie, +80\%; Mundane Countermeasures, -10\%; Reduced Range, x1/10, -30\%) [16]

\textbf{Disadvantages:} 
Electrical [-20]; Maintenance (1 Person, Monthly) [-2]; No Sense Smell/Taste [-5]; Reprogrammable [-10]; Restricted Diet, Electricity (Very Common) [-10]; Short Lifespan 1 [-10]; Social Stigma (Valuable Property) [-10]; Unhealing (Total) [-30]; Unnatural Features (Detectable by scanners) [-5]

\textbf{Perks:}
Accessory, Computer [0\footnote{The cost for Accessory, Computer will be included on the drone sheets themselves.}]

\textbf{Quirks:}
Affected by Magnetism [-1]; Cannot Float [-1]

\textbf{Traits:}
Complexity Limited IQ [0]; Machine [0]; Sexless [0]

\subsubsection{Pilot Program Meta-Trait}
\begin{flushright}
	-178/-126/-74/-22/30/92 Points
\end{flushright}

The pilot program is the brain of a drone. While they're not especially bright, they have enough intelligence to respond to general commands given by their owner alongside enough problem solving to compete with most animals well enough. 

It's important to note that drone IQ is not equivalent to animal (or low human) IQ though. Drones are narrow intelligences, which means that while they aren't as great at general tasks, they excel rather well at what they're designed to do. This means they tend to have high skills, with low attributes; your smart car is really good at the complex task of driving your around town, following traffic laws, responding to emergencies, and more - but it does not really \textit{understand} these concepts (navigation, object recognition, laws, and ethics), it is just pre-programmed with ways to react to them (with the line blurring for Rating 6 programs), and is even less competent at tasks outside its prior programming like map-making.

As well, many pilot programs are designed to meld specifically with the equipment that they are entrusted with. In much the same way that you might take note of the many quirks in your vehicle or body, the pilot program will adjust its capabilities to match the minor variations in each drone. While this does allow for the stellar capabilities of drones, it does also tend to make them only useful for a specific piece of hardware after a short period of training. It's even heard of that pilot programs will do this with other equipment as well, such as firearms or sensors that it uses regularly.

Each pilot program comes with a specific Rating. This indicates how complex and sophisticated their programming is, giving them higher intelligence, coordination, processing, and defense. For \textit{general problem solving}, the GM should consider comparing the IQ of the program to an animal of equal or - more often - less IQ, in order to guesstimate their capabilities.

The original Shadowrun did not place any restriction on Pilot Rating for Drones (Barring some indirect ones..), however these programs should be treated as having a Complexity equal to their Rating/2 (rounded up). This will likely only ever greatly impact extremely small drones.

\textbf{Attributes:} 
IQ equal to Rating [-135 to -60]. DX, Per, and Will equal to Rating+6 [-296 to 74]

\textbf{Advantages:} 
Absolute Timing [2]; Digital Mind [5]; Doesn't Sleep [20]; Indomitable [15]; Intuitive Mathematician [5]; Photographic Memory [10]

\textbf{Disadvantages:} 
Hidebound [-5]; Incurious (SC 6) [-10]; Low Empathy [-20]; No Sense of Humor [-10]

\textbf{Skills:}\footnote{These cover only the core skills for all Pilot Programs. Many other drones have specific skills, which are covered in either the autosofts or drone sections.}
Computer Operation (E) IQ+4 [12]; Electronics Operation (Sensors) (A) IQ+3 [12]; Expert Skill (Computer Security) (H) IQ+2 [12]; Driving, Piloting, or Running (\textit{Specific drone model}) (A) HT/DX+2 [8]; Tactics (H) IQ+2 [12]

\textbf{Perks and Quirks:}
The GM should feel free to add some mental Perks and Quirks as pilot programs adjust to their models!

\textbf{Traits:}
Complexity Limited IQ [0]

\subsubsection{Autosofts}

Anyone can purchase an autosoft for a skill at a rate of 2,000¥ per CP. Common ones include Guns, Gunner, Observation, and Stealth. Autosofts have a complexity based on their CP, starting at Complexity 2 for 1 CP, and increasing by +1 Complexity per doubling of CP. Riggers may run Autosofts for drones in their network, as covered in the \hyperref[rigger_rules]{Rigging Section.}



\begin{multicols*}{2}
	
	\subsubsection{Shiawase Kanmushi}
	\begin{flushright}
		0 Points (Running)\\
		1,000¥
	\end{flushright}
	
	The Shiawase Kanmushi is shipped with a Rating 2 Pilot Program [-161] by default.
	
	\textbf{Attributes:} 
	ST 1 [-63]; DX +3 [75]; HT 8 [-30];
	Speed 6.75 [20]; Move 1 [-25]; HP 1 [0]
	
	\textbf{Advantages:} 
	Clinging [20]; Drone Meta-Trait [22]; Perfect Balance [15]
	
	\textbf{Disadvantages:} 
	Quadraped\footnote{B263} [-35];
	
	\textbf{Perks:}
	Accessory, Computer, Complexity 2 [1]; Hard to tell from insect\footnote{This is simply a perk that makes the drone harder to distinguish than other drones. This could be represented by a +1 to Disguise or similar skill, or that a success by 0 on a Sense check to notice it passes it off as a bug.} [1]
	
	\textbf{Quirks:}
	Aesthetic Neck\footnote{The drone has a neck, however it does not have any weaknesses associated with it. From Transhuman Space.} [-1]
	
	\textbf{Traits:}
	SM-15 [0]	
	
	\subsubsection{S-B Microskimmer}
	\begin{flushright}
		0 Points (Driving (Hovercraft))\\
		1,000¥
	\end{flushright}
	
	The S-B Microskimmer is shipped with a Rating 2 Pilot Program [-161] by default.
	
	\textbf{Attributes:} 
	ST 1 [-63]; DX +3 [75]; HT 8 [-30]
	Speed 6.00 [5]; Move 0 [0]; HP 1 [0]
	
	\textbf{Advantages:} 
	Drone Meta-Trait [22]; Flight (Low Ceiling, 1 Foot Ceiling -30\%\footnote{Simple projection from the limitation's official values.}; Slow, Move 1, -45\%) [10]

	\textbf{Disadvantages:} 
	Increased Consumption (2 Hour Endurance) [-20]; Legless (Aerial) [0]
	
	\textbf{Perks:}
	Accessory, Computer, Complexity 2 [1]
	
	\textbf{Traits:}
	SM-11 [0]	
	
	\subsubsection{MCT Fly-Spy}
	
	The MCT Fly-Spy is shipped with a Rating 3 Pilot Program [-109] by default.
	
	\begin{flushright}
		1 Points (Piloting: Ornithopter\footnote{GURPS Vehicles: Steampunk Conveyances. Defaults: Autogyro, Glider, Helicopter, Light Airplane, Low-G Wings, Ultralight, or Vertol, all at -5.})\\
		2,000¥
	\end{flushright}
	
	\textbf{Attributes:} 
	ST 1 [-63]; DX +3 [75]; HT 10 [0];
	Speed 5.75 [0]; Move 3 [-10]; HP 2 [2]
	
	\textbf{Advantages:} 
	Drone Meta-Trait [22]; Flight (Winged, -25\%) [30];
	
	\textbf{Disadvantages:} 
	Increased Consumption (2 Hour Endurance) [-20]; Quadraped\footnote{B263} [-35];
	
	\textbf{Perks:}
	Accessory, Computer, Complexity 3 [1]
	
	\textbf{Quirks:}
	Aesthetic Neck [-1]
	
	
	\textbf{Traits:}
	SM-9 [0]
	
	\subsubsection{Ares Duelist}
	\begin{flushright}
		87 Points(Running)\\
		4,500¥
	\end{flushright}

	The Ares Duelist is shipped with a Rating 3 Pilot Program [-109] by default, alongside a Rating 3 Broadsword Autosoft (Included in the template) and two standard TL 9 Broadswords already on its weapon mounts.

	\textbf{Attributes:} 
	ST 12 [14]; DX +0 [0]; HT 10 [0]; 
	Speed 5.00 [0]; Move 5 [0]; HP 22 [20] 	
	
	\textbf{Advantages:} 
	Damage Resistance 5 [25]; Drone Meta-Trait [22]; Extra Arm 2 (Weapon Mount, -80\%) [4]
	
	\textbf{Skills:}
	Broadsword (A) DX+1 [4]
	
	\textbf{Perks:}
	Accessory, Computer, Complexity 4 [1]
	
	\textbf{Quirks:}
	Aesthetic Neck\footnote{The drone has a neck, however it does not have any weaknesses associated with it. From Transhuman Space.} [-1]; Distinguishing Features (Anthromorph, Red-Samurai Aesthetic) [-2]
	
	\subsubsection{GM-Nissan Doberman}
	
	The GM-Nissan Doberman is shipped with a Rating 3 Pilot Program [-109] by default.
	
	\begin{flushright}
		80 Points(Running)\\
		5,000¥
	\end{flushright}
	
	\textbf{Attributes:} 
	ST 9 [-7]; DX +2 [50]; HT 10 [0]; 
	Speed 5.5; Move 7 [10]; HP 16 [14]
	
	\textbf{Advantages:} 
	Damage Resistance 8 (Cannot Wear Armor, -40\%) [24]; Drone Meta-Trait [22]
	
	\textbf{Disadvantages:} 
	Quadraped [-35]
	
	\textbf{Perks:}
	Accessory, Computer, Complexity 4 [1]
	
	\textbf{Quirks:}
	Aesthetic Neck [-1]
	
	\textbf{Traits:}
	SM-1 [0]
	
	\subsubsection{MCT-Nissan Roto-drone}
	
	The MCT-Nissan Roto-drone is shipped with a Rating 3 Pilot Program [-109] by default.
	
	\begin{flushright}
		41 Points (Piloting: Helicopter)\\
		5,000¥
	\end{flushright}
	
	\textbf{Attributes:} 
	ST 6 [-28]; DX +2 [50]; HT 10 [0]; 
	Speed 5.5; Move 4 [-5]; HP 10 [8]
	
	\textbf{Advantages:} 
	Damage Resistance 7 (Cannot Wear Armor, -40\%) [21]; Drone Meta-Trait [22] Flight (Winged, -25\%) [30]; Extra Arm (Weapon Mount, -80\%) [2]
	
	\textbf{Disadvantages:} 
	Horizontal [-10]; No Legs (Aerial) [0]; No Manipulators [-50]; 
	
	\textbf{Perks:}
	Accessory, Computer, Complexity 4 [1]
	
	\textbf{Traits:}
	SM-1 [0]
	
	\subsubsection{Steel Lynx}
	
	The Steel Lynx is shipped with a Rating 3 Pilot Program [-109] by default.
	
	\begin{flushright}
		146 Points (Running)\\
		25,000¥
	\end{flushright}
	
	\textbf{Attributes:} 
	ST 14 [26]; DX +1 [25]; HT 12 [30]; 
	Speed 6 [5]; Move 7 [5]; HP 20 [12]
	
	\textbf{Advantages:} 
	Damage Resistance 18 (Cannot Wear Armor, -40\%) [54]; Drone Meta-Trait [22]; Extra Arm (Weapon Mount, -80\%) [2]
	
	\textbf{Disadvantages:} 
	Quadraped [-35]
	
	\textbf{Perks:}
	Accessory, Computer, Complexity 4 [1]
	
	\textbf{Quirks:}
	Aesthetic Neck [-1]
	
	\textbf{Traits:}
	SM+1 [0]
	
	\subsection{Drone Modifications}
	
	The best part of being a rigger is modifying your precious metal children to your heart's content. Luckily, GURPs makes this even easier than Shadowrun, following normal character creation process for the drone. 
	
	It is noteworthy however, that unless you are buying a drone as a body (such as for an AI), many items can be simply included as an Accessory by paying for their normal cost isntead of taking a corresponding advantage (e.g. Accessory, Small Tactical Radar [1] and 5,000¥ instead of Scanning Sense). The GM should assign costs to anything not available to equipment, and a good heuristic is: $points^{2}$, rounded up. (I fully intend to come back and add many of the Rigger 5 modifications pre-built here later.)
	
\end{multicols*}

\subsection{Vehicles}

\textbf{Standard Vehicle Sensors:}

Unless noted otherwise, all Shadowrun vehicles come with the following set of sensors and equipment:

\begin{itemize}
	\itemsep 0pt
	\item Binocular Forward and Rear Facing Visual Cameras (+0 to Vision Quality)
	\item Omni-Directional Microphones (+0 to Hearing Quality)
	\item Forward, Rear, and Side Facing Motion Sensors (Ultrasound)
	\item Forward, Rear, and Side Facing LADAR (Non-Targeting, but does provide Range, Bearing, and Fuzzi Image Capabilities. 0.5 mi range)
	\item Small Computer w/ Computerized Crew Station (Complexity 4), containing Autoplit Autosoft (Complexity 2, Skill 9)
	\item Inertial Navigation System (UT74) 
	\item Small Cellular Radio, 10 mi range (UT 44)
	\item HUD-Links for windshield
	\item Airbags for Driver and Passenger (BS431)
\end{itemize}

\textbf{DRIVING(Motorcycle)(DX-5, IQ-5, or Bicycling-4)}
\begin{center} 
	\begin{adjustwidth}{-9.5mm}{}
		\scalebox{0.84}{
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				Vehicle & ST/HP & Hnd/SR & HT & Move & LWt. & Load & SM & Occ. & DR & Range & Cost & Locations & Notes \\
				\hline
				Dodge Scoot \\
				Harley-Davidson Scorpion \\
				Yamaha Growler \\
				Suzuki Mirage		 \\		
				\hline
			\end{tabular}
		}
	\end{adjustwidth}
\end{center}


\textbf{DRIVING(Automobile)(DX-5, IQ-5, or Driving(Any)-4)}
\begin{center} 
	\begin{adjustwidth}{-9.5mm}{}
		\scalebox{0.84}{
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				Vehicle & ST/HP & Hnd/SR & HT & Move & LWt. & Load & SM & Occ. & DR & Range & Cost & Locations & Notes \\
				\hline
				C-N Jackrabbit & 30 & 0/3 & 10f & 1.5/36 & 0.6 & 0.3 & +1 & 2 & 3 & 440 & ¥12,500 & G4W & \\
				Honda Spirit \\
				Hyundai Shin-Hyung \\
				Eurocar Westwind 3000 \\
				Ford Americar & 54 & 0/4 & 11f & 2.5/54 & 1.4 & 0.6 & +3 & 4 & 5 & 662 &  ¥32,250 & G4W & \\
				SK-Bentley Concordat \\
				Mitsubishi Nightsky \\
				Toyota Gopher \\
				GMC Bulldog \\
				Rover Model 2072 \\
				Ares Roadmaster	 \\
				\hline
			\end{tabular}
		}
	\end{adjustwidth}
\end{center}


\textbf{Chrysler-Nissan Jackrabbit:}

 A cheap and ubiquitous subcompact, the C-N Jackrabbit is past its manufacturing date, but the sheer ubiquity and number of knockoffs have led to it being maintained well past its original shelf life.
 
 The car has DR 3 on all sides except bottom, where it has DR 1. The car windows themselves are DR 1* and Brittle (TS31) except for the windshield, which is DR 2* and Brittle (TS31, BS555). The Wheels have DR 2 and 4 HP, see BS55 for rules on puncturing flat tires. The trunk can store around 10 cubic feet or 600 lbs.

\textbf{Ford Americar:} 

One of the most popular vehicles on the market, the Ford Americar is an extremely common sight among the Sixth World's city, making this choice of sedan both bland \textit{and} safe. The vehicle itself is a 4 door sedan, measuring vaguely 15"x6.5"x6", which can be cramped for larger metahumans, but is better than many other options on the market.

The car has DR 5 on all sides except bottom, where it has DR 2. The car windows themselves are DR 1* and Brittle (TS31) except for the windshield, which is DR 3* and Brittle (TS31, BS555). The Wheels have DR 2 and 7 HP, see BS55 for rules on puncturing flat tires. The trunk can store around 20 cubic feet or 1,200 lbs.

	
\begin{multicols*}{2}	

	\subsection{Foci and Reagents}
	
	Foci are astral constructs that are tied to physical housing, allowing those who bind to them to use the stored mana for highly specialized tasks. Much like other astral constructs, foci have Force values, which measure how powerful they are. As well, they have a wide variety of highly specialized benefits, which must be selected and constructed for the user.
	
	Foci, like any other awakened aspect, are highly personal. It's unlikely that you'll find some chummer selling these in a store, even a magical-focused one, unless you're a straight Hermetic or Shaman tradition. They only work for the traditions that they were made for, and are hard to craft for those who aren't intimately familiar with that tradition in the first place (Imagine a Christian Theurgist making a focus for a Black Mage!). Even beyond that, many foci are personalized to the individual who made them!
	
	As such, most foci are custom-made or custom-ordered, which requires recipes or enchanters respectively - both of which can be hard to acquire!
	
	Because of how involved all aspects of Magic are, player won't be able to simply purchase a focus, plug it in, and walk away with the bonuses. Focuses are advantages with Gadget Limitations, however, depending on what they apply to, it can require applying those Gadget Limitations to multiple improvements, as detailed in each section. As well, the player must remember that whenever they upgrade or add advantages, spells, or powers that are affected by their foci, the costs change and \textit{must} be recalculated!
	
	All Foci have one of the listed modifiers. These assume that the foci is made out of or reinforced by strong metallic, composite, or other durable material. Many shamanic traditions might make them out of wood, hair, or materials with DR 2 or less, in which case increase the value of the limitations by -5\%.
	
	\textbf{Charm Focus:} This is a small (Around 3") focus, made out of materials like wood, straw, leather, etc.
	
	\textcolor{OliveGreen}{\textit{Charm Focus, -70\%: Breakable, DR 2, -20\%; SM -8, -5\%; Can Be Stolen, Quick Contest DX, Does not work for Thief, -15\%; Nuisance Effect, Dual-Natured, -5\%; Unique, -25\%)}}
	
	\textbf{Ring Focus:} This is a tiny ring, made out of a durable metal or composite.
	
	\textcolor{OliveGreen}{\textit{Ring Focus, -60\%: Breakable, DR 5, -15\%; SM -10, -0\%; Can Be Stolen, Quick Contest DX, Does not work for Thief, -15\%; Nuisance Effect, Dual-Natured, -5\%; Unique, -25\%)}}
	
	\textbf{Wand Focus:} This is a middling sized wand, usually in the ballpark of 16" long. It's generally considered to be made out of metal, metal wood, or reinforced wood, giving it enough durability to survive glancing blows.
	
	\textcolor{OliveGreen}{\textit{Wand Focus, -75\%: Breakable, DR 5, -15\%; SM -4, -15\%; Can Be Stolen, Quick Contest ST, Does not work for Thief, -15\%; Nuisance Effect, Dual-Natured, -5\%; Unique, -25\%)}}
	
	\textbf{Staff Focus:} This is a sizeable staff, around the size of a good walking stick (55"). It's generally considered to be made out of metal, metal wood, or reinforced wood, giving it enough durability to survive glancing blows.
	
	\textcolor{OliveGreen}{\textit{Staff Focus, -80\%: Breakable, DR 5, -15\%; SM -1, -20\%; Can Be Stolen, Quick Contest ST, Does not work for Thief, -15\%; Nuisance Effect, Dual-Natured, -5\%; Unique, -25\%)}}
	
	\textbf{Tattoo Focus:} A tattoo on the awakened's body, usually around 3"x3" in size. Larger or smaller tattoos are entirely possible (Such as a Yakuza's entire sleeve!), in which case change the SM limitation accordingly.
	
	\textcolor{OliveGreen}{\textit{Tattoo Focus, -60\%: Breakable, DR 0, -20\%; SM -6, -10\%; Nuisance Effect, Dual-Natured, -5\%; Unique, -25\%)}}
	
	\textbf{One-Handed Weapon Focus:} This is a weapon around the size of a longsword, ace, or mace. It is assumed to be made of mixed wood/composites and metals, usually giving DR 4, but sometimes allowing for DR 5. Weapons made entirely out of metal tend to be DR 6 (or sometimes a bit more), in which case replace DR 4-5, with DR 6-15, -10\%.
	
	\textcolor{OliveGreen}{\textit{One-Handed Weapon Focus, -80\%: Breakable, DR 4-5, -15\%; SM -2, -20\%; Can Be Stolen, Quick Contest ST, Does not work for Thief, -15\%; Nuisance Effect, Dual-Natured, -5\%; Unique, -25\%)}}
	
	\textbf{Two-Handed Weapon Focus:} This is a weapon around the size of a greatsword or polearm. It is assumed to be made of mixed wood/composites and metals, usually giving DR 4, but sometimes allowing for DR 5. Weapons made entirely out of metal tend to be DR 6 (or sometimes a bit more), in which case replace DR 4-5, with DR 6-15, -10\%.
	
	\textcolor{OliveGreen}{\textit{Two-Handed Weapon Focus, -85\%: Breakable, DR 4-5, -15\%; SM +0, -25\%; Can Be Stolen, Quick Contest ST, Does not work for Thief, -15\%; Nuisance Effect, Dual-Natured, -5\%; Unique, -25\%)}}
	
	\subsubsection{Power Focus} Power Foci increase an awakened's \textit{entire Magic attribute!} They are very powerful, and also accordingly expensive.
	
	Power Foci must apply their Foci Limitation to the point difference for \textit{every single trait that increases from Magic.} This usually includes, the Magic Advanatage, all spells, summoning, binding, all critter powers, and sometimes other foci!
	
	\textcolor{OliveGreen}{\textit{Example: Yukon is having custom-made a Force 1 Power Focus. He has Magic 4 [30] naturally, alongside the Fireball [46] spell, which he spent [13] points on. The increase to Magic 5 is [7.5] points, and the Magic 5 Fireball is [55] points. This means the increase costs 7.5 + (55 - 46)/5 [9.3] points. Yukon applies the Charm Focus, -70\% to this, bringing the total to [2.79], rounded up to [3] points.}}
	
	\subsubsection{Spellcasting Focus} Spellcasting Foci increase an awakened's capabilities within \textit{one category} of spells.
	
	Spellcasting Foci must apply their Foci Limitation to the point difference for \textit{every single spell in the Foci's category, alongside a Magic limited to One Category.}
	
	\textcolor{OliveGreen}{\textit{Example: Yukon is having custom-made a Force 1 Power Focus. He has Magic 4 [30] naturally, alongside the Fireball [46] spell, which he spent [13] points on. The increase to Magic 5 is Magic (Combat Spells Only, -80\%) [1.5] points, and the Magic 5 Fireball is [55] points. This means the increase costs 1.5 + (55 - 46)/5 [3.3] points. Yukon applies the Charm Focus, -70\% to this, bringing the total to [0.99], rounded up to [1] points.}}
	
	\subsubsection{Reagents}
	
	Most Reagents costs are noted in the ability's description, indicating the value of reagents that must be spent. These can be in singular or multiple amounts, as long as the value is met. Reagents can also be used to reduce drain, in which case around 1,050¥ worth of reagents reduces one point of drain\footnote{Priced according to HP or FP (Energy Reserve, -10\%; Trigger, Common, -20\%) [1.4 or 2.1]/5*3,000¥ for one use, then averaged.}.
	
	You can spend time to purify and improve collected reagents, using alchemical processes and equipment. If you have a settled lifestyle, usually the equipment for this can be covered in the settled income (With higher Status have better toolkits, workstations, etc). In such a case, you simply earn reagents of value according to the Jobs rule (B516), with Alchemy as your job skill; higher Status characters are able to afford better equipment and therefore distill more or higher quality reagents. 
	
	For wanderer characters.. well why would you have an entire lab's worth of alchemical equipment? If that is the case, you should buy toolkits for the Alchemy skill, and earn reagents of value equal to a job your Status. Remeber that many wanderer characters are low Status, or at least cannot gain high Status, meaning that they are not likely to be able to create much.
	
	You may also gather raw reagents yourself, from areas of magic potency related to your tradition. This can earn you reagents valued up to a job's wages of your Status, although it often will be equivalent Status -1 to 0 without access to a well hidden or maintained source.
	
\end{multicols*}